### 2015-06-08 ms.tex
First commit with empty ms and makefile

% Telluric modeling in Keck/HIRES iodine spectra

\documentclass{emulateapj}
\usepackage{amsmath,amssymb}
\usepackage{xspace}
\usepackage{graphicx}
\bibliographystyle{apj}
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{natbib}
\citestyle{aa}
\usepackage{verbatim}
\usepackage{morefloats} % somehow need this to have lots of figures
                        % and tables?
% for attractive links:
\usepackage[colorlinks,urlcolor=blue,citecolor=black,linkcolor=blue]{hyperref}
%\usepackage[nolists]{endfloat} % put floats at end - doesn't work
\interfootnotelinepenalty=10000 % Do not want cross-page footnote!

% chinese character for name
\usepackage{CJK}

\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\bcm{\begin{comment}}
\def\ecm{\end{comment}}
\def\mps{m~s$^{-1}$}
\def\msini{M\sin{i}}
\def\mjup{M_{\rm Jup}}
\def\msol{M_{\odot}}

\slugcomment{}
\shorttitle{}
\shortauthors{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{CJK*}{UTF8}{gbsn}

\title
{
The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine
Cell as Calibrators\altaffilmark{1}
}

\altaffiltext{1}
{
Based on observations observations obtained at the Keck Observatory, which is operated
by the University of California.  The Keck Observatory was made
possible by the generous financial support of the W. M. Keck
Foundation.
}

\author{Sharon Xuesong Wang (王雪凇)\altaffilmark{2,3},
  Jason T. Wright\altaffilmark{2,3}} % primary work force
\author{Chad Bender\altaffilmark{2,3}} % lots of help with TERRASPEC
                                % and consultation on telluric lines
\author{Andrew W. Howard\altaffilmark{4}} % Keck
\author{Geoffrey W. Marcy\altaffilmark{5}} % Keck
\author{Howard Isaacson\altaffilmark{5}} % Keck
\author{Suvrath Mahadevan\altaffilmark{2,3}} % comments and suggestions

\altaffiltext{2}{Department of Astronomy and Astrophysics, 525 Davey
  Laboratory, The Pennsylvania State University, University Park, PA
  16802, USA; Send correspondence to xxw131@psu.edu and
  jtwright@astro.psu.edu}

\altaffiltext{3}{Center for Exoplanets and Habitable Worlds, 525 Davey
  Laboratory, The Pennsylvania State University, University Park, PA
  16802, USA}

\altaffiltext{4}{Hawaii, USA}

\altaffiltext{5}{Department of Astronomy, University of California,
  Berkeley, CA 94720, USA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Tellurics are bad and you really don't want them. Here's how to get
rid of them.

\end{abstract}

\keywords{instrumentation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

I'll keep the first paragraph so there are some references -- also
because it's cool. Jupiter analogs orbiting other stars represent the first signposts of
true Solar System analogs, and the eccentricity distribution of these
planets with $a>3$ AU will reveal how rare or frequent true Jupiter
analogs are. To date, only 9 ``Jupiter analogs" have been
well-characterized in the peer reviewed literature\footnote{HD
  13931$b$ \citep{2010ApJ...721.1467H}, HD 72659$b$
  \citep{2011A&A...527A..63M}, 55 Cnc $d$ \citep{2002ApJ...581.1375M},
  HD 134987$c$ \citep{2010MNRAS.403.1703J}, HD 154345$b$ \citep[but
    with possibility of being an activity cycle-induced
    signal]{2008ApJ...683L..63W}, $\mu$ Ara $c$
  \citep{2007A&A...462..769P}, HD 183263$c$
  \citep{2009ApJ...693.1084W}, HD 187123$c$
  \citep{2009ApJ...693.1084W}, and GJ 832$b$
  \citep{2009ApJ...690..743B}.}  \citep[defined here as $P > 8$ years,
  $4 > M\sin{i} > 0.5\ \mjup$, and $e <
  0.3$;][exoplanets.org]{wrighteod}. As the duration of existing
planet searches approach 10--20 years, more and more Jupiter analogs
will emerge from their longest-observed targets
\citep{2012arXiv1205.2765W, 2012arXiv1205.5835B}.

%----------------------------------------------------------------
% SME Parameters Table
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable}{lc}
\tabletypesize{\scriptsize}
\tablecaption{STELLAR PARAMETERS\label{smetable}}
\tablewidth{180pt}
\tablehead{
  \colhead{Parameter} & \colhead{Value~~}
}
\startdata
~~Spectral type\tablenotemark{a} & K0 V ~~ \\
~~Distance (pc)\tablenotemark{a} & 44.0 $\pm$ 2.1 ~~ \\
~~$V$ & 8.661 $\pm$ 0.013 ~~ \\
%$B-V$           &   ~~ \\ % not seen B-V in Jeff's SME file
~~$T_{\mbox{eff}}$ (K) & 5448 $\pm $44 ~~ \\
~~$\log{g}$ & 4.511 $\pm$ 0.024 ~~ \\
~~$[$Fe/H$]$ & 0.336 $\pm$ 0.030 ~~ \\
%~~$v\sin{i}$ (k\mps) & 0.14 $\pm$ 0.5 ~~ \\ % no detection available
~~BC & -0.144 ~~ \\
~~$M_{\mbox{bol}}$ & 5.301 ~~ \\
~~$L_{\star}$ ($L_{\odot}$) & 0.590 $\pm$ 0.058 ~~ \\
~~$R_{\star}$ ($R_{\odot}$) & 0.901 $\pm$ 0.015 ~~ \\
~~$M_{\star}$ ($\msol$) & 1.000 $\pm$ 0.017 ~~ \\
~~$v\sin{i}$ & $<1$ k\mps ~~ \\
~~Age\tablenotemark{b}  & $\sim 7$ Gyr ~~
%S$_{HK}$         &   ~~ \\
%log$R'_{HK}$     &   ~~ \\
%$P_{rot}$ (days) &
\enddata
\tablenotetext{a}{\cite{esa1997,vanleeuwen2008}.}
\tablenotetext{b}{\cite{svalue2010}, see section.}
\end{deluxetable}
%----------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Then Acknowledgement
% Thank John Johnson for providing CPS Doppler code.
\acknowledgements
% John
The authors thank John A. Johnson for providing a copy of his Doppler
code and his help with our incorporation of the code into the HET
pipeline.  The authors also thank Debra Fischer for her assistance in
this regard.

% CEHW
This work was partially supported by funding from the Center for
Exoplanets and Habitable Worlds, which is supported by the
Pennsylvania State University, the Eberly College of Science, and the
Pennsylvania Space Grant Consortium.

% Financial support acknowledgement
The authors appreciate the significant Keck observing time and
associated funding support from NASA for the study of long period
planets and mulitplanet systems.
%
J.T.W.\ and S.X.W.\ acknowledge support from NASA Origins of Solar
Systems grant NNX10AI52G.

% Keck
The work herein is based on observations obtained at the W. M. Keck
Observatory, which is operated jointly by the University of California
and the California Institute of Technology.  The Keck Observatory was
made possible by the generous financial support of the W.M. Keck
Foundation.  We wish to recognize and acknowledge the very significant
cultural role and reverence that the summit of Mauna Kea has always
had within the indigenous Hawaiian community.  We are most fortunate
to have the opportunity to conduct observations from this mountain.

% HET
The Hobby-Eberly Telescope is a joint project of the University of
Texas at Austin, the Pennsylvania State University, Stanford
University, Ludwig Maximillians Universit\"at M\"unchen, and Georg
August Universit\"at G\"ottingen. The HET is named in honor of its
principal benefactors, William P. Hobby and Robert E. Eberly.

% ADS
This work has made use NASA’s Astrophysics Data System Bibliographic Services.

\end{CJK*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Bibliography
%\bibliographystyle{apj} % (uses file "xxx.bst")
%\bibliography{mn-jour,references}%,bootstrap-ref}
\bibliography{references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2015-07-31 simulation/ms.tex
Make subdirectory for paper focusing on simulation.

--- 2015-06-08 ms.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{sec:intro}
 
-I'll keep the first paragraph so there are some references -- also
-because it's cool. Jupiter analogs orbiting other stars represent the first signposts of
-true Solar System analogs, and the eccentricity distribution of these
-planets with $a>3$ AU will reveal how rare or frequent true Jupiter
-analogs are. To date, only 9 ``Jupiter analogs" have been
-well-characterized in the peer reviewed literature\footnote{HD
-  13931$b$ \citep{2010ApJ...721.1467H}, HD 72659$b$
-  \citep{2011A&A...527A..63M}, 55 Cnc $d$ \citep{2002ApJ...581.1375M},
-  HD 134987$c$ \citep{2010MNRAS.403.1703J}, HD 154345$b$ \citep[but
-    with possibility of being an activity cycle-induced
-    signal]{2008ApJ...683L..63W}, $\mu$ Ara $c$
-  \citep{2007A&A...462..769P}, HD 183263$c$
-  \citep{2009ApJ...693.1084W}, HD 187123$c$
-  \citep{2009ApJ...693.1084W}, and GJ 832$b$
-  \citep{2009ApJ...690..743B}.}  \citep[defined here as $P > 8$ years,
-  $4 > M\sin{i} > 0.5\ \mjup$, and $e <
-  0.3$;][exoplanets.org]{wrighteod}. As the duration of existing
-planet searches approach 10--20 years, more and more Jupiter analogs
-will emerge from their longest-observed targets
-\citep{2012arXiv1205.2765W, 2012arXiv1205.5835B}.
+We are going to cite \cite{artigau2014, cunha2014} and \cite{hitran2013}.
 
-%----------------------------------------------------------------
-% SME Parameters Table
-\renewcommand{\arraystretch}{1.2} % more row spacing for the table
-\begin{deluxetable}{lc}
-\tabletypesize{\scriptsize}
-\tablecaption{STELLAR PARAMETERS\label{smetable}}
-\tablewidth{180pt}
-\tablehead{
-  \colhead{Parameter} & \colhead{Value~~}
-}
-\startdata
-~~Spectral type\tablenotemark{a} & K0 V ~~ \\
-~~Distance (pc)\tablenotemark{a} & 44.0 $\pm$ 2.1 ~~ \\
-~~$V$ & 8.661 $\pm$ 0.013 ~~ \\
-%$B-V$           &   ~~ \\ % not seen B-V in Jeff's SME file
-~~$T_{\mbox{eff}}$ (K) & 5448 $\pm $44 ~~ \\
-~~$\log{g}$ & 4.511 $\pm$ 0.024 ~~ \\
-~~$[$Fe/H$]$ & 0.336 $\pm$ 0.030 ~~ \\
-%~~$v\sin{i}$ (k\mps) & 0.14 $\pm$ 0.5 ~~ \\ % no detection available
-~~BC & -0.144 ~~ \\
-~~$M_{\mbox{bol}}$ & 5.301 ~~ \\
-~~$L_{\star}$ ($L_{\odot}$) & 0.590 $\pm$ 0.058 ~~ \\
-~~$R_{\star}$ ($R_{\odot}$) & 0.901 $\pm$ 0.015 ~~ \\
-~~$M_{\star}$ ($\msol$) & 1.000 $\pm$ 0.017 ~~ \\
-~~$v\sin{i}$ & $<1$ k\mps ~~ \\
-~~Age\tablenotemark{b}  & $\sim 7$ Gyr ~~
-%S$_{HK}$         &   ~~ \\
-%log$R'_{HK}$     &   ~~ \\
-%$P_{rot}$ (days) &
-\enddata
-\tablenotetext{a}{\cite{esa1997,vanleeuwen2008}.}
-\tablenotetext{b}{\cite{svalue2010}, see section.}
-\end{deluxetable}
-%----------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data and Data Analysis Tools}\label{sec:data}
+
+Introduction to Keck/HIRES CPS data, data reduction, Doppler code. Our
+adoption of Doppler code.
+
+Introduction to the standard star(s) in this paper?
+
+ZZZ Table: standard star stellar properties? esp. coordinates to
+highlight BC ranges?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Effects of Telluric Lines}\label{sec:effects}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulated Data}
+
+This is where TERRASPEC got introduced.
+
+ZZZ Plots:
+
+- telluric line atlas in the optical? just to demonstrate where they are.
+
+- telluric free simulations to demonstrate RV precision, vs. year,
+vs. BC
+
+- telluric injected simulations to demonstrate effects, vs. year, vs. BC
+
+- RV vs. BC for chunks with and without telluric lines before and
+after injection
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{On-Sky Data}
+
+Should this be the first?
+
+ZZZ Plots:
+
+- RV vs. year/time, RV vs. BC
+
+- RV from chunks with and without telluric lines, vs. BC
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Where and How Telluric Lines Enter the Data}
+
+Should this subsection be moved to the first?
+It enters the epoch data as well as the empirically derived stellar template.
+
+ZZZ Plots:
+
+- fitting plots showing data (with telluric highlighted) and DSST
+(tellurics highlighted) and the mismatch
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Correcting for the Effects of Telluric Lines}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Masking out the Telluric Lines}
+
+ZZZ Plot:
+
+- Illustration of choice of mask
+
+- RV vs. BC before and after for all, telluric, and non-telluric chunks
+
+- simulation results showing no aliases introduced by masking
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Removing the Telluric Contamination from Stellar Templates}
+
+ZZZ Plot:
+
+- selected chunk before and after cleaning
+
+- ?RV vs. BC using cleaned template, no masking, single mask?, double mask?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Modeling Telluric Lines in the Star$+$Iodine Spectra}
+
+ZZZ Plot:
+
+- RV vs. BC using cleaned template plus full telluric modeling
+
+- RV vs. BC using cleaned template plus full modeling plus some masking?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Results for A Different RV Standard Star}
+
+I think this is a must! At least one more star, hopefully two.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Future Work}\label{sec:summary}
+
+Gaussian processes!
 

### 2015-07-31 simulation/ms.tex
First skeleton for simulation draft.

@@
-% Telluric modeling in Keck/HIRES iodine spectra
+% Effects of telluric lines, as demonstrated via simulation
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data and Data Analysis Tools}\label{sec:data}
+\section{Methodology}\label{sec:method}
 
-Introduction to Keck/HIRES CPS data, data reduction, Doppler code. Our
-adoption of Doppler code.
+Introduction to Keck/HIRES CPS data,
 
-Introduction to the standard star(s) in this paper?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulated Keck/HIRES Spectra}
 
-ZZZ Table: standard star stellar properties? esp. coordinates to
-highlight BC ranges?
+ZZZ Plots:
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Effects of Telluric Lines}\label{sec:effects}
+- comparison between simulated and observed Keck/HIRES spectra: blaze,
+and zoom in.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simulated Data}
+- comparison between SME stellar template and empirical, deconvolved
+template.
 
-This is where TERRASPEC got introduced.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Injection of Telluric Lines}
+
+Description of TERRASPEC.
 
@@
 - telluric line atlas in the optical? just to demonstrate where they are.
+
+- simulated observation and template with injected tellurics,
+overplotted with clean simulated spectra, which would also demonstrate
+that due to BC, lines will pull on each other.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Extraction of Radial Velocities}
+
+Introduction to Doppler code and relevant adoption part for the
+simulation.
+
+How the end product RVs are computed (vanking, or other weighting schemes).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Effects of Telluric Lines on RV Precision}
+
+ZZZ Plots:
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{On-Sky Data}
-
-Should this be the first?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Remedies and Their Effectiveness}
 
@@
 
-- RV vs. year/time, RV vs. BC
+- demonstration of effectiveness and ineffectiveness of double masking.
 
-- RV from chunks with and without telluric lines, vs. BC
+- demonstration of effectiveness of a clean template and forward
+modeling tellurics.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Where and How Telluric Lines Enter the Data}
-
-Should this subsection be moved to the first?
-It enters the epoch data as well as the empirically derived stellar template.
-
-ZZZ Plots:
-
-- fitting plots showing data (with telluric highlighted) and DSST
-(tellurics highlighted) and the mismatch
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correcting for the Effects of Telluric Lines}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Masking out the Telluric Lines}
-
-ZZZ Plot:
-
-- Illustration of choice of mask
-
-- RV vs. BC before and after for all, telluric, and non-telluric chunks
-
-- simulation results showing no aliases introduced by masking
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Removing the Telluric Contamination from Stellar Templates}
-
-ZZZ Plot:
-
-- selected chunk before and after cleaning
-
-- ?RV vs. BC using cleaned template, no masking, single mask?, double mask?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Modeling Telluric Lines in the Star$+$Iodine Spectra}
-
-ZZZ Plot:
-
-- RV vs. BC using cleaned template plus full telluric modeling
-
-- RV vs. BC using cleaned template plus full modeling plus some masking?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Results for A Different RV Standard Star}
-
-I think this is a must! At least one more star, hopefully two.
+- demonstration of precision required for modeling tellurics, and
+maximum tolerance for template `cleaness'.
 
@@
 
-Gaussian processes!
+Work on actual observations!
 

### 2015-07-31 ms.tex
Back up the master ms.tex which has skeleton for all work.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{sec:intro}
 
-I'll keep the first paragraph so there are some references -- also
-because it's cool. Jupiter analogs orbiting other stars represent the first signposts of
-true Solar System analogs, and the eccentricity distribution of these
-planets with $a>3$ AU will reveal how rare or frequent true Jupiter
-analogs are. To date, only 9 ``Jupiter analogs" have been
-well-characterized in the peer reviewed literature\footnote{HD
-  13931$b$ \citep{2010ApJ...721.1467H}, HD 72659$b$
-  \citep{2011A&A...527A..63M}, 55 Cnc $d$ \citep{2002ApJ...581.1375M},
-  HD 134987$c$ \citep{2010MNRAS.403.1703J}, HD 154345$b$ \citep[but
-    with possibility of being an activity cycle-induced
-    signal]{2008ApJ...683L..63W}, $\mu$ Ara $c$
-  \citep{2007A&A...462..769P}, HD 183263$c$
-  \citep{2009ApJ...693.1084W}, HD 187123$c$
-  \citep{2009ApJ...693.1084W}, and GJ 832$b$
-  \citep{2009ApJ...690..743B}.}  \citep[defined here as $P > 8$ years,
-  $4 > M\sin{i} > 0.5\ \mjup$, and $e <
-  0.3$;][exoplanets.org]{wrighteod}. As the duration of existing
-planet searches approach 10--20 years, more and more Jupiter analogs
-will emerge from their longest-observed targets
-\citep{2012arXiv1205.2765W, 2012arXiv1205.5835B}.
+We are going to cite \cite{artigau2014, cunha2014} and \cite{hitran2013}.
 
-%----------------------------------------------------------------
-% SME Parameters Table
-\renewcommand{\arraystretch}{1.2} % more row spacing for the table
-\begin{deluxetable}{lc}
-\tabletypesize{\scriptsize}
-\tablecaption{STELLAR PARAMETERS\label{smetable}}
-\tablewidth{180pt}
-\tablehead{
-  \colhead{Parameter} & \colhead{Value~~}
-}
-\startdata
-~~Spectral type\tablenotemark{a} & K0 V ~~ \\
-~~Distance (pc)\tablenotemark{a} & 44.0 $\pm$ 2.1 ~~ \\
-~~$V$ & 8.661 $\pm$ 0.013 ~~ \\
-%$B-V$           &   ~~ \\ % not seen B-V in Jeff's SME file
-~~$T_{\mbox{eff}}$ (K) & 5448 $\pm $44 ~~ \\
-~~$\log{g}$ & 4.511 $\pm$ 0.024 ~~ \\
-~~$[$Fe/H$]$ & 0.336 $\pm$ 0.030 ~~ \\
-%~~$v\sin{i}$ (k\mps) & 0.14 $\pm$ 0.5 ~~ \\ % no detection available
-~~BC & -0.144 ~~ \\
-~~$M_{\mbox{bol}}$ & 5.301 ~~ \\
-~~$L_{\star}$ ($L_{\odot}$) & 0.590 $\pm$ 0.058 ~~ \\
-~~$R_{\star}$ ($R_{\odot}$) & 0.901 $\pm$ 0.015 ~~ \\
-~~$M_{\star}$ ($\msol$) & 1.000 $\pm$ 0.017 ~~ \\
-~~$v\sin{i}$ & $<1$ k\mps ~~ \\
-~~Age\tablenotemark{b}  & $\sim 7$ Gyr ~~
-%S$_{HK}$         &   ~~ \\
-%log$R'_{HK}$     &   ~~ \\
-%$P_{rot}$ (days) &
-\enddata
-\tablenotetext{a}{\cite{esa1997,vanleeuwen2008}.}
-\tablenotetext{b}{\cite{svalue2010}, see section.}
-\end{deluxetable}
-%----------------------------------------------------------------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Simulating Keck/HIRES Spectra}\label{sec:simulating}
+
+Introduction to Keck/HIRES CPS data, data reduction, Doppler code. Our
+adoption of Doppler code.
+
+Introduction to the standard star(s) in this paper?
+
+ZZZ Table: standard star stellar properties? esp. coordinates to
+highlight BC ranges?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Injecting Telluric Lines}\label{sec:injecting}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulated Data}
+
+This is where TERRASPEC got introduced.
+
+ZZZ Plots:
+
+- telluric line atlas in the optical? just to demonstrate where they are.
+
+- telluric free simulations to demonstrate RV precision, vs. year,
+vs. BC
+
+- telluric injected simulations to demonstrate effects, vs. year, vs. BC
+
+- RV vs. BC for chunks with and without telluric lines before and
+after injection
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{On-Sky Data}
+
+Should this be the first?
+
+ZZZ Plots:
+
+- RV vs. year/time, RV vs. BC
+
+- RV from chunks with and without telluric lines, vs. BC
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Where and How Telluric Lines Enter the Data}
+
+Should this subsection be moved to the first?
+It enters the epoch data as well as the empirically derived stellar template.
+
+ZZZ Plots:
+
+- fitting plots showing data (with telluric highlighted) and DSST
+(tellurics highlighted) and the mismatch
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Correcting for the Effects of Telluric Lines}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Masking out the Telluric Lines}
+
+ZZZ Plot:
+
+- Illustration of choice of mask
+
+- RV vs. BC before and after for all, telluric, and non-telluric chunks
+
+- simulation results showing no aliases introduced by masking
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Removing the Telluric Contamination from Stellar Templates}
+
+ZZZ Plot:
+
+- selected chunk before and after cleaning
+
+- ?RV vs. BC using cleaned template, no masking, single mask?, double mask?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Modeling Telluric Lines in the Star$+$Iodine Spectra}
+
+ZZZ Plot:
+
+- RV vs. BC using cleaned template plus full telluric modeling
+
+- RV vs. BC using cleaned template plus full modeling plus some masking?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Results for A Different RV Standard Star}
+
+I think this is a must! At least one more star, hopefully two.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Future Work}\label{sec:summary}
+
+Gaussian processes!
 

### 2015-08-05 simulation/ms.tex
Add Jason's suggestions in simulation/ms.tex

@@
 
-We are going to cite \cite{artigau2014, cunha2014} and \cite{hitran2013}.
+We are going to cite \cite{artigau2014, cunha2014} and
+\cite{hitran2013}.
+
+Jason's suggestions:
+
+- run tau Ceti as target #2
+
+- don't show our classic before+after+difference RV vs. BC, just show
+the difference, especially the talk
+
+- show actual data for sig Dra RV vs. BC of Keck, to show that this is
+real, it should be standard to plot RV vs. BC to check systematics
+(i.e. tellurics)
+
+- Mention Vogt APF paper sig Dra planet.
 

### 2016-02-03 telluric/ms.tex
Change simulation/ to telluric/. Rough text and structure for telluric paper.

--- 2015-07-31 simulation/ms.tex
@@
 
-Tellurics are bad and you really don't want them. Here's how to get
+Tellurics are bad and you really don't want them. Here's why and how to get
 rid of them.
@@
 
-We are going to cite \cite{artigau2014, cunha2014} and \cite{hitran2013}.
+The radial velocity method has contributed to hundreds of planetary
+discoveries and Kepler follow-ups. The current precision is at 1--2
+m/s, with limiting factor being stellar activity and RV systematics,
+instrumental or software.
+
+One of the contributing term comes from Earth's atmospheric
+absorption, which imprints telluric lines onto the observed stellar
+spectrum. Deep tellurics are thrown out, while micro-tellurics
+(define; \citealt{hitran2013}) remain and they are very hard to deal
+with. The contamination from the micro-telluric lines has an adverse
+effect on the RV precision, and such effect is characterized for the
+HARPS-N spectrograph, which is ThAr calibrated, by \cite{artigau2014}
+and \cite{cunha2014}.
+
+In this paper, we characterize and discuss the remedies for
+micro-telluric lines in the context of iodine-calibarted precise
+RVs. We first quantify the effects of micro-telluric contamination on
+RV precision through simulation. Then we discuss possible remedies and
+their effectiveness. Finally we discuss implementation on real data
+and future work.
+
+\begin{comment}
+Jason's suggestions:
+- run tau Ceti as target #2
+- don't show our classic before+after+difference RV vs. BC, just show
+the difference, especially the talk
+- show actual data for sig Dra RV vs. BC of Keck, to show that this is
+real, it should be standard to plot RV vs. BC to check systematics
+(i.e. tellurics)
+- Mention Vogt APF paper sig Dra planet.
+\end{comment}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methodology}\label{sec:method}
+\section{Impacts of Micro-tellurics on RV Precision}\label{sec:method}
 
-Introduction to Keck/HIRES CPS data,
+We performed end-to-end simulation of Keck data and analysis process
+to access the impacts of micro-tellurics on RV precision. We use Keck
+to demonstrate this because Keck has the highest precision. We chose
+sig Dra and tau Ceti as our stars because they are RV standards which
+have been observed hundreds of times with Keck/HIRES, and are also
+favorite RV standards at other precise RV facilities. I really want to
+add an M dwarf standard here as well!
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Simulated Keck/HIRES Spectra}
+\subsection{Methodology}
 
-ZZZ Plots:
+We simulated Keck observations on sig Dra and tau Ceti by using
+synthetic stellar spectra of their respective spectral types (?) using
+SME (ZZZ cite Valenti and Fischer). We simulated one spectrum for each
+actual observed spectrum taken at Keck through the CPS programs. The
+synthetic stellar spectra is multiplied with the iodine atlas to
+create the standard iodine$+$ star RV observations. The multiplied
+spectrum is then multiplied with the blaze function and convolved with
+the observed spectral PSF, both derived from real observations for
+each night. Poisson noise is added.
 
-- comparison between simulated and observed Keck/HIRES spectra: blaze,
-and zoom in.
+We then forward model the simulated spectra to extract RVs using the
+CPS Keck code (ZZZ cite Johnson and Howard). We used the synthetic
+stellar spectrum as the input stellar template. In reality, stellar
+templates are derived from observed stellar spectra via deconvolution,
+which would introduce additional errors. Using the same synthetic
+stellar spectrum would eliminate such errors and isolate the problem
+to telluric lines only.
 
-- comparison between SME stellar template and empirical, deconvolved
-template.
+We ran two sets of simulations: control and contaminated. In the
+control, we only had stellar spectrum and iodine spectrum. In the
+contaminated, we added in simulated telluric lines in the simulated
+observed spectrum. The telluric lines were generated using TERRASPEC
+(ZZZ cite Bender). We adopted the typical Mauna Kea atmospheric
+condition (temperature and pressure profiles) and typical oxygen
+column density (which in realiaty flucturate very little anyway). For
+simplicity, we assumed the same water column density for every
+observation, which is pwv$=1$mm, a little bit humid than a typical
+Mauna Kea night (true? I think this is actually pretty typical). The
+pair of simulated control and contaminated spectra have the same added
+Poisson noise, and therefore any RV differences derived from these two
+sets of simulation would reveal the net effect of telluric
+contamination.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Injection of Telluric Lines}
+\subsection{Results}
 
-Description of TERRASPEC.
+Plots: RV difference vs. BC for sig Dra and tau Ceti. And M stars.
 
-ZZZ Plots:
+Micro-tellurics in the iodine region introduces RMS$=0.6$ m/s scatter
+for GK stars (RV systematic error added in quadrature). Leaving
+untreated, this would define the precision floor.
 
-- telluric line atlas in the optical? just to demonstrate where they are.
+Additionally, it manifests as spurious signal at periods of a sidereal
+year and harmonics, with an amplitude of 20 cm/s. This would affect
+our ability to detect super-Earth in the habitable zone of GK stars
+(Earth's signal is 8 cm/s). We have seen such spurious signal in Keck
+data on many stars, and telluric contamination is one of the
+contributing factors (see discussion for other factors).
 
-- simulated observation and template with injected tellurics,
-overplotted with clean simulated spectra, which would also demonstrate
-that due to BC, lines will pull on each other.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Extraction of Radial Velocities}
-
-Introduction to Doppler code and relevant adoption part for the
-simulation.
-
-How the end product RVs are computed (vanking, or other weighting schemes).
+For M stars... (probably worse)
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Remedies and Effectiveness}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Effects of Telluric Lines on RV Precision}
+Plots: effects of full forward modeling (RV difference between modeled
+and contaminated, modeled and control).
 
-ZZZ Plots:
+We demonstrate the effectiveness of several remedies. First, double
+masking: probably a terrible idea. Describe the effects
+quantitatively. Second, modeling plus cleaning tempaltes: probably
+effective. Modeling plus some masking?
 
-- telluric free simulations to demonstrate RV precision, vs. year,
-vs. BC
-
-- telluric injected simulations to demonstrate effects, vs. year, vs. BC
-
-- RV vs. BC for chunks with and without telluric lines before and
-after injection
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Remedies and Their Effectiveness}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
 

### 2016-02-24 telluric/ms.tex
Last two sections for tellurics paper.

@@
 
+Modeling telluric lines itself is a challeging task. ZZZ Cite the
+paper TERRASPEC and simular softwares and their 2\% modeling
+precision. Cite Lockwood, Bender et al.\ for 1\% in L band. ZZZ
+
 In this paper, we characterize and discuss the remedies for
@@
 We demonstrate the effectiveness of several remedies. First, double
-masking: probably a terrible idea. Describe the effects
-quantitatively. Second, modeling plus cleaning tempaltes: probably
-effective. Modeling plus some masking?
+masking: probably a terrible idea. Throwing away the pixels will make
+the fitter harder to converge, and introduce additional errors on the
+scales larger than the effects of telluric lines
+themselves. Additionally, it is hard to choose a flux cut-off
+level. Throwing away too much would mean unstable solution and lower
+RV precision, but masking too little would mean insufficient
+removal of tellurics.
+
+Second, full forward modeling plus some sort of masking for deep
+lines. This is the most effective way. Modeling precision of
+$\sim$90\% basically bring the adverse effects of tellurics down to
+$<$10 cm/s. 90\% is very easy to achieve -- remember the
+state-of-the-art is 1-2\%, and even consider errors induced by
+modeling residuals caused by atmospheric wind or lack of knowledge on
+linelist or broadening parameters or inaccurate knowledge on atmospheric
+temperature/pressure profiles. The deep lines may not be modeled very
+well. However, the statistical weighting procedure at the very end
+will empirically quantify which chunks behave badly due to ineffective
+modeling of telluric lines and thus throw out or de-weigh the chunks.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\section{Discussion and Future Work}\label{sec:future}
 
-ZZZ Plots:
+In terms of application to real observations, this brings marginal
+improvements to existing Keck data. We tested on sig Dra, tau Ceti,
+and M stars, the differences are...
 
-- demonstration of effectiveness and ineffectiveness of double masking.
-
-- demonstration of effectiveness of a clean template and forward
-modeling tellurics.
-
-- demonstration of precision required for modeling tellurics, and
-maximum tolerance for template `cleaness'.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Future Work}\label{sec:summary}
-
-Work on actual observations!
+Important for MINERVA, HRS2, HPF2. Crucial for CARMENES, HPF, EPDS, SHREK,
+ESPRESSO, SPiRou etc. White paper has suggested improvement on line
+lists in HITRAN. EPRV2 has a lot of recommendations. That is the
+future direction.
 

### 2016-02-29 telluric/ms.tex
First couple paragraphs for tellurics intro and citations.

@@
 \def\msol{M_{\odot}}
+\def\kepler{{\it Kepler}}
 
@@
 The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine
-Cell as Calibrators\altaffilmark{1}
+Cells as Calibrators\altaffilmark{1}
 }
@@
 {
-Based on observations observations obtained at the Keck Observatory, which is operated
-by the University of California.  The Keck Observatory was made
-possible by the generous financial support of the W. M. Keck
-Foundation.
+Based on observations observations obtained at the Keck Observatory,
+which is operated by the University of California. The Keck
+Observatory was made possible by the generous financial support of the
+W. M. Keck Foundation.
 }
@@
 
-The radial velocity method has contributed to hundreds of planetary
-discoveries and Kepler follow-ups. The current precision is at 1--2
-m/s, with limiting factor being stellar activity and RV systematics,
-instrumental or software.
+The first exoplanets around main-sequence stars were discovered by the
+radial velocity (RV) method, where precise Doppler spectroscopy
+measures the wavelength shift of the host stars induced by the
+gravitational pull of the planets \citep{1988ApJ...331..902C,
+  1989Natur.339...38L, 1993ApJ...413..339H, 1995Natur.378..355M,
+  1996ApJ...464L.153B}. Since then, the RV method has discovered
+hundreds of planetary systems (see exoplanets.org; \citealt{eod2014})
+and contributed to numerous confirmation and characterization of
+exoplanets discovered by the transit method (e.g., for
+\kepler\ follow-up observations; \citealt{Marcy2014}).
+
+The current best RV precision is around 1~m/s, attainable via two
+wavelength calibration methods: ThAr lamp emission line calibration
+(e.g., ELODIE and HARPS; \citealt{elodie, harps-s}) and iodine cell
+absorption line calibration (e.g., Keck/HIRES; \citealt{butler1996}).
 

### 2016-03-01 telluric/ms.tex
More text in telluric introduction.

@@
 
-The current best RV precision is around 1~m/s, attainable via two
-wavelength calibration methods: ThAr lamp emission line calibration
-(e.g., ELODIE and HARPS; \citealt{elodie, harps-s}) and iodine cell
-absorption line calibration (e.g., Keck/HIRES; \citealt{butler1996}).
+The current best RV precision is around 1~m/s \citep{eprv2015},
+attainable via two wavelength calibration methods in the optical band:
+ThAr lamp emission line calibration (e.g., ELODIE and HARPS;
+\citealt{elodie, harps-s}; $\sim$400-690~nm) and iodine cell
+absorption line calibration (e.g., Keck/HIRES and Magellan/PFS;
+\citealt{butler1996, 2010SPIE.7735E..53C}; $\sim$500-620~nm). The
+major obstacles for achieving a higher RV precision are: stellar
+activity induced RV signals, instrumental effects, telluric
+contamination, and limitation in data analysis \citep{eprv2015}.
 
-One of the contributing term comes from Earth's atmospheric
-absorption, which imprints telluric lines onto the observed stellar
-spectrum. Deep tellurics are thrown out, while micro-tellurics
-(define; \citealt{hitran2013}) remain and they are very hard to deal
-with. The contamination from the micro-telluric lines has an adverse
-effect on the RV precision, and such effect is characterized for the
-HARPS-N spectrograph, which is ThAr calibrated, by \cite{artigau2014}
-and \cite{cunha2014}.
+Traditionally, telluric contamination is not considered as problematic
+for precise RV in the optical. It is certainly a sever source of
+spectral contamination and a bottleneck for achieving higher RV
+precision in the near infra-red region (e.g.,
+\citealt{2010ApJ...713..410B}), where a large number of deep water and
+methane lines reside. However, there is only a small wavelength
+range in the optical that has deep telluric lines, and typically such
+regions are simply thrown out for the purpose of precise RV analysis,
+either by giving them zero weights in the cross correlation masks (for
+ThAr calibrated spectra, e.g., \citealt{2002A&A...388..632P}) or
+flagging them as bad pixels (for iodine calibrated spectra, e.g., for
+Keck/HIRES).
+
+Recently, the works by \cite{artigau2014} and \cite{cunha2014} have
+characterized and mitigated the effects of telluric contamination in
+the precise RV data taken by the ThAr-calibrated HARPS-S.
+\cite{cunha2014} focuses on the issues with ``micro-telluric" lines
+(shallow telluric absorption lines with $<1$-3\% depths), which are
+recognized for the first time. \cite{cunha2014} fit and then divide
+out the telluric lines in the observed spectra using synthetic
+telluric spectra generated by the LBLRTM package (Line-By-Line
+Radiative Transfer Model, \citealt{lblrtm}; with line lists from
+HIgh-resolution TRANsmission molecular absorption database, or HITRAN,
+\citealt{hitran2013}) and also TAPAS \citep{tapas}, which is a more
+user-friendly but less flexible package wrapper using LBLRTM. They
+concluded that the micro-tellurics have an impact (defined as RMS of
+difference between RVs before and after micro-telluric removal) of
+$\sim$10-20 cm/s for G stars observed with low to moderate air masses,
+but the impact can be substantial in some cases to up to $\sim$0.5-1
+m/s. \cite{artigau2014} uses principal component analysis (PCA) to
+empirically correct for telluric lines in HARPS-S data (both
+micro-tellurics and the deep lines in the $\sim$630~nm region), and
+combined PCA with rejection masking, they reduced the RV RMS by
+$\sim$20~cm/s (and more significantly for the $\sim$630~nm region).
+
+% I'm here:
+This paper focuses on the adverse effects of telluric contamination
+and its remedies under the context of iodine-calibrated precise RV,
+especially for ``micro-telluric" lines (shallow telluric absorption
+lines with $<1$-3\% depths; \citealt{cunha2014}). As for spectral
+region contaminated with deep telluric lines, typical precise RV
+analysis usually gives
+
+Previously, \cite{cunha2014} have characterized the effects of
+micro-telluric contamination and proposed solution for the
+ThAr-calibrated HARPS-S data.
 

### 2016-03-02 telluric/ms.tex
First finished draft on tellurics introduction except for the last paragraph.

@@
 spectral contamination and a bottleneck for achieving higher RV
-precision in the near infra-red region (e.g.,
+precision in the near infra-red (NIR) region (e.g.,
 \citealt{2010ApJ...713..410B}), where a large number of deep water and
@@
 but the impact can be substantial in some cases to up to $\sim$0.5-1
-m/s. \cite{artigau2014} uses principal component analysis (PCA) to
+m/s.
+
+\cite{artigau2014} uses principal component analysis (PCA) to
 empirically correct for telluric lines in HARPS-S data (both
@@
 combined PCA with rejection masking, they reduced the RV RMS by
-$\sim$20~cm/s (and more significantly for the $\sim$630~nm region).
+$\sim$20~cm/s (and more significantly for the $\sim$630~nm
+region). More recently, \cite{2016AAS...22713719S} characterized the
+effects of telluric contamination and effectiveness of some typical
+remedies (masking and modeling) for emission line-calibarated spectra
+for the optical, broad optical (300-900~nm), and NIR. Their conclusion
+for the optical region is similar to the results in \cite{artigau2014}
+and \cite{cunha2014}.
 
-% I'm here:
-This paper focuses on the adverse effects of telluric contamination
-and its remedies under the context of iodine-calibrated precise RV,
-especially for ``micro-telluric" lines (shallow telluric absorption
-lines with $<1$-3\% depths; \citealt{cunha2014}). As for spectral
-region contaminated with deep telluric lines, typical precise RV
-analysis usually gives
-
-Previously, \cite{cunha2014} have characterized the effects of
-micro-telluric contamination and proposed solution for the
-ThAr-calibrated HARPS-S data.
-
-Modeling telluric lines itself is a challeging task. ZZZ Cite the
-paper TERRASPEC and simular softwares and their 2\% modeling
-precision. Cite Lockwood, Bender et al.\ for 1\% in L band. ZZZ
-
-In this paper, we characterize and discuss the remedies for
-micro-telluric lines in the context of iodine-calibarted precise
-RVs. We first quantify the effects of micro-telluric contamination on
-RV precision through simulation. Then we discuss possible remedies and
-their effectiveness. Finally we discuss implementation on real data
-and future work.
-
-\begin{comment}
-Jason's suggestions:
-- run tau Ceti as target #2
-- don't show our classic before+after+difference RV vs. BC, just show
-the difference, especially the talk
-- show actual data for sig Dra RV vs. BC of Keck, to show that this is
-real, it should be standard to plot RV vs. BC to check systematics
-(i.e. tellurics)
-- Mention Vogt APF paper sig Dra planet.
-\end{comment}
+This paper characterizes and corrects for the adverse effects of
+telluric contamination under the context of iodine-calibrated precise
+RV, especially for the micro-telluric lines. ZZZ We first describe our
+methodology for characterizing the effects of tellurics in
+Section~\ref{sec:method}, then... ZZZ
 

### 2016-03-30 telluric/ms.tex
Move main text to telluric.tex for easier copy to thesis.

--- 2016-02-29 telluric/ms.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}\label{sec:intro}
-
-The first exoplanets around main-sequence stars were discovered by the
-radial velocity (RV) method, where precise Doppler spectroscopy
-measures the wavelength shift of the host stars induced by the
-gravitational pull of the planets \citep{1988ApJ...331..902C,
-  1989Natur.339...38L, 1993ApJ...413..339H, 1995Natur.378..355M,
-  1996ApJ...464L.153B}. Since then, the RV method has discovered
-hundreds of planetary systems (see exoplanets.org; \citealt{eod2014})
-and contributed to numerous confirmation and characterization of
-exoplanets discovered by the transit method (e.g., for
-\kepler\ follow-up observations; \citealt{Marcy2014}).
-
-The current best RV precision is around 1~m/s, attainable via two
-wavelength calibration methods: ThAr lamp emission line calibration
-(e.g., ELODIE and HARPS; \citealt{elodie, harps-s}) and iodine cell
-absorption line calibration (e.g., Keck/HIRES; \citealt{butler1996}).
-
-One of the contributing term comes from Earth's atmospheric
-absorption, which imprints telluric lines onto the observed stellar
-spectrum. Deep tellurics are thrown out, while micro-tellurics
-(define; \citealt{hitran2013}) remain and they are very hard to deal
-with. The contamination from the micro-telluric lines has an adverse
-effect on the RV precision, and such effect is characterized for the
-HARPS-N spectrograph, which is ThAr calibrated, by \cite{artigau2014}
-and \cite{cunha2014}.
-
-Modeling telluric lines itself is a challeging task. ZZZ Cite the
-paper TERRASPEC and simular softwares and their 2\% modeling
-precision. Cite Lockwood, Bender et al.\ for 1\% in L band. ZZZ
-
-In this paper, we characterize and discuss the remedies for
-micro-telluric lines in the context of iodine-calibarted precise
-RVs. We first quantify the effects of micro-telluric contamination on
-RV precision through simulation. Then we discuss possible remedies and
-their effectiveness. Finally we discuss implementation on real data
-and future work.
-
-\begin{comment}
-Jason's suggestions:
-- run tau Ceti as target #2
-- don't show our classic before+after+difference RV vs. BC, just show
-the difference, especially the talk
-- show actual data for sig Dra RV vs. BC of Keck, to show that this is
-real, it should be standard to plot RV vs. BC to check systematics
-(i.e. tellurics)
-- Mention Vogt APF paper sig Dra planet.
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Impacts of Micro-tellurics on RV Precision}\label{sec:method}
-
-We performed end-to-end simulation of Keck data and analysis process
-to access the impacts of micro-tellurics on RV precision. We use Keck
-to demonstrate this because Keck has the highest precision. We chose
-sig Dra and tau Ceti as our stars because they are RV standards which
-have been observed hundreds of times with Keck/HIRES, and are also
-favorite RV standards at other precise RV facilities. I really want to
-add an M dwarf standard here as well!
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Methodology}
-
-We simulated Keck observations on sig Dra and tau Ceti by using
-synthetic stellar spectra of their respective spectral types (?) using
-SME (ZZZ cite Valenti and Fischer). We simulated one spectrum for each
-actual observed spectrum taken at Keck through the CPS programs. The
-synthetic stellar spectra is multiplied with the iodine atlas to
-create the standard iodine$+$ star RV observations. The multiplied
-spectrum is then multiplied with the blaze function and convolved with
-the observed spectral PSF, both derived from real observations for
-each night. Poisson noise is added.
-
-We then forward model the simulated spectra to extract RVs using the
-CPS Keck code (ZZZ cite Johnson and Howard). We used the synthetic
-stellar spectrum as the input stellar template. In reality, stellar
-templates are derived from observed stellar spectra via deconvolution,
-which would introduce additional errors. Using the same synthetic
-stellar spectrum would eliminate such errors and isolate the problem
-to telluric lines only.
-
-We ran two sets of simulations: control and contaminated. In the
-control, we only had stellar spectrum and iodine spectrum. In the
-contaminated, we added in simulated telluric lines in the simulated
-observed spectrum. The telluric lines were generated using TERRASPEC
-(ZZZ cite Bender). We adopted the typical Mauna Kea atmospheric
-condition (temperature and pressure profiles) and typical oxygen
-column density (which in realiaty flucturate very little anyway). For
-simplicity, we assumed the same water column density for every
-observation, which is pwv$=1$mm, a little bit humid than a typical
-Mauna Kea night (true? I think this is actually pretty typical). The
-pair of simulated control and contaminated spectra have the same added
-Poisson noise, and therefore any RV differences derived from these two
-sets of simulation would reveal the net effect of telluric
-contamination.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Results}
-
-Plots: RV difference vs. BC for sig Dra and tau Ceti. And M stars.
-
-Micro-tellurics in the iodine region introduces RMS$=0.6$ m/s scatter
-for GK stars (RV systematic error added in quadrature). Leaving
-untreated, this would define the precision floor.
-
-Additionally, it manifests as spurious signal at periods of a sidereal
-year and harmonics, with an amplitude of 20 cm/s. This would affect
-our ability to detect super-Earth in the habitable zone of GK stars
-(Earth's signal is 8 cm/s). We have seen such spurious signal in Keck
-data on many stars, and telluric contamination is one of the
-contributing factors (see discussion for other factors).
-
-For M stars... (probably worse)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Remedies and Effectiveness}
-
-Plots: effects of full forward modeling (RV difference between modeled
-and contaminated, modeled and control).
-
-We demonstrate the effectiveness of several remedies. First, double
-masking: probably a terrible idea. Throwing away the pixels will make
-the fitter harder to converge, and introduce additional errors on the
-scales larger than the effects of telluric lines
-themselves. Additionally, it is hard to choose a flux cut-off
-level. Throwing away too much would mean unstable solution and lower
-RV precision, but masking too little would mean insufficient
-removal of tellurics.
-
-Second, full forward modeling plus some sort of masking for deep
-lines. This is the most effective way. Modeling precision of
-$\sim$90\% basically bring the adverse effects of tellurics down to
-$<$10 cm/s. 90\% is very easy to achieve -- remember the
-state-of-the-art is 1-2\%, and even consider errors induced by
-modeling residuals caused by atmospheric wind or lack of knowledge on
-linelist or broadening parameters or inaccurate knowledge on atmospheric
-temperature/pressure profiles. The deep lines may not be modeled very
-well. However, the statistical weighting procedure at the very end
-will empirically quantify which chunks behave badly due to ineffective
-modeling of telluric lines and thus throw out or de-weigh the chunks.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Future Work}\label{sec:future}
-
-In terms of application to real observations, this brings marginal
-improvements to existing Keck data. We tested on sig Dra, tau Ceti,
-and M stars, the differences are...
-
-Important for MINERVA, HRS2, HPF2. Crucial for CARMENES, HPF, EPDS, SHREK,
-ESPRESSO, SPiRou etc. White paper has suggested improvement on line
-lists in HITRAN. EPRV2 has a lot of recommendations. That is the
-future direction.
+\input{telluric.tex}
 

### 2016-03-30 telluric/telluric.tex
Move main text to telluric.tex for easier copy to thesis.

% main text for the telluric paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

The first exoplanets around main-sequence stars were discovered by the
radial velocity (RV) method, where precise Doppler spectroscopy
measures the wavelength shift of the host stars induced by the
gravitational pull of the planets \citep{1988ApJ...331..902C,
  1989Natur.339...38L, 1993ApJ...413..339H, 1995Natur.378..355M,
  1996ApJ...464L.153B}. Since then, the RV method has discovered
hundreds of planetary systems (see exoplanets.org; \citealt{eod2014})
and contributed to numerous confirmation and characterization of
exoplanets discovered by the transit method (e.g., for
\kepler\ follow-up observations; \citealt{Marcy2014}).

The current best RV precision is around 1~m/s \citep{eprv2015},
attainable via two wavelength calibration methods in the optical band:
ThAr lamp emission line calibration (e.g., ELODIE and HARPS;
\citealt{elodie, harps-s}; $\sim$400-690~nm) and iodine cell
absorption line calibration (e.g., Keck/HIRES and Magellan/PFS;
\citealt{butler1996, 2010SPIE.7735E..53C}; $\sim$500-620~nm). The
major obstacles for achieving a higher RV precision are: stellar
activity induced RV signals, instrumental effects, telluric
contamination, and limitation in data analysis \citep{eprv2015}.

Traditionally, telluric contamination is not considered as problematic
for precise RV in the optical. It is certainly a sever source of
spectral contamination and a bottleneck for achieving higher RV
precision in the near infra-red (NIR) region (e.g.,
\citealt{2010ApJ...713..410B}), where a large number of deep water and
methane lines reside. However, there is only a small wavelength
range in the optical that has deep telluric lines, and typically such
regions are simply thrown out for the purpose of precise RV analysis,
either by giving them zero weights in the cross correlation masks (for
ThAr calibrated spectra, e.g., \citealt{2002A&A...388..632P}) or
flagging them as bad pixels (for iodine calibrated spectra, e.g., for
Keck/HIRES).

Recently, the works by \cite{artigau2014} and \cite{cunha2014} have
characterized and mitigated the effects of telluric contamination in
the precise RV data taken by the ThAr-calibrated HARPS-S.
\cite{cunha2014} focuses on the issues with ``micro-telluric" lines
(shallow telluric absorption lines with $<1$-3\% depths), which are
recognized for the first time. \cite{cunha2014} fit and then divide
out the telluric lines in the observed spectra using synthetic
telluric spectra generated by the LBLRTM package (Line-By-Line
Radiative Transfer Model, \citealt{lblrtm}; with line lists from
HIgh-resolution TRANsmission molecular absorption database, or HITRAN,
\citealt{hitran2013}) and also TAPAS \citep{tapas}, which is a more
user-friendly but less flexible package wrapper using LBLRTM. They
concluded that the micro-tellurics have an impact (defined as RMS of
difference between RVs before and after micro-telluric removal) of
$\sim$10-20 cm/s for G stars observed with low to moderate air masses,
but the impact can be substantial in some cases to up to $\sim$0.5-1
m/s.

\cite{artigau2014} uses principal component analysis (PCA) to
empirically correct for telluric lines in HARPS-S data (both
micro-tellurics and the deep lines in the $\sim$630~nm region), and
combined PCA with rejection masking, they reduced the RV RMS by
$\sim$20~cm/s (and more significantly for the $\sim$630~nm
region). More recently, \cite{2016AAS...22713719S} characterized the
effects of telluric contamination and effectiveness of some typical
remedies (masking and modeling) for emission line-calibarated spectra
for the optical, broad optical (300-900~nm), and NIR. Their conclusion
for the optical region is similar to the results in \cite{artigau2014}
and \cite{cunha2014}.

This paper characterizes and corrects for the adverse effects of
telluric contamination under the context of iodine-calibrated precise
RV, especially for the micro-telluric lines. ZZZ We first describe our
methodology for characterizing the effects of tellurics in
Section~\ref{sec:method}, then... ZZZ

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Impacts of Micro-tellurics on RV Precision}\label{sec:method}

We performed end-to-end simulation of Keck data and analysis process
to access the impacts of micro-tellurics on RV precision. We use Keck
to demonstrate this because Keck has the highest precision. We chose
sig Dra and tau Ceti as our stars because they are RV standards which
have been observed hundreds of times with Keck/HIRES, and are also
favorite RV standards at other precise RV facilities. I really want to
add an M dwarf standard here as well!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Methodology}

We simulated Keck observations on sig Dra and tau Ceti by using
synthetic stellar spectra of their respective spectral types (?) using
SME (ZZZ cite Valenti and Fischer). We simulated one spectrum for each
actual observed spectrum taken at Keck through the CPS programs. The
synthetic stellar spectra is multiplied with the iodine atlas to
create the standard iodine$+$ star RV observations. The multiplied
spectrum is then multiplied with the blaze function and convolved with
the observed spectral PSF, both derived from real observations for
each night. Poisson noise is added.

We then forward model the simulated spectra to extract RVs using the
CPS Keck code (ZZZ cite Johnson and Howard). We used the synthetic
stellar spectrum as the input stellar template. In reality, stellar
templates are derived from observed stellar spectra via deconvolution,
which would introduce additional errors. Using the same synthetic
stellar spectrum would eliminate such errors and isolate the problem
to telluric lines only.

We ran two sets of simulations: control and contaminated. In the
control, we only had stellar spectrum and iodine spectrum. In the
contaminated, we added in simulated telluric lines in the simulated
observed spectrum. The telluric lines were generated using TERRASPEC
(ZZZ cite Bender). We adopted the typical Mauna Kea atmospheric
condition (temperature and pressure profiles) and typical oxygen
column density (which in realiaty flucturate very little anyway). For
simplicity, we assumed the same water column density for every
observation, which is pwv$=1$mm, a little bit humid than a typical
Mauna Kea night (true? I think this is actually pretty typical). The
pair of simulated control and contaminated spectra have the same added
Poisson noise, and therefore any RV differences derived from these two
sets of simulation would reveal the net effect of telluric
contamination.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results}

Plots: RV difference vs. BC for sig Dra and tau Ceti. And M stars.

Micro-tellurics in the iodine region introduces RMS$=0.6$ m/s scatter
for GK stars (RV systematic error added in quadrature). Leaving
untreated, this would define the precision floor.

Additionally, it manifests as spurious signal at periods of a sidereal
year and harmonics, with an amplitude of 20 cm/s. This would affect
our ability to detect super-Earth in the habitable zone of GK stars
(Earth's signal is 8 cm/s). We have seen such spurious signal in Keck
data on many stars, and telluric contamination is one of the
contributing factors (see discussion for other factors).

For M stars... (probably worse)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Remedies and Effectiveness}

Plots: effects of full forward modeling (RV difference between modeled
and contaminated, modeled and control).

We demonstrate the effectiveness of several remedies. First, double
masking: probably a terrible idea. Throwing away the pixels will make
the fitter harder to converge, and introduce additional errors on the
scales larger than the effects of telluric lines
themselves. Additionally, it is hard to choose a flux cut-off
level. Throwing away too much would mean unstable solution and lower
RV precision, but masking too little would mean insufficient
removal of tellurics.

Second, full forward modeling plus some sort of masking for deep
lines. This is the most effective way. Modeling precision of
$\sim$90\% basically bring the adverse effects of tellurics down to
$<$10 cm/s. 90\% is very easy to achieve -- remember the
state-of-the-art is 1-2\%, and even consider errors induced by
modeling residuals caused by atmospheric wind or lack of knowledge on
linelist or broadening parameters or inaccurate knowledge on atmospheric
temperature/pressure profiles. The deep lines may not be modeled very
well. However, the statistical weighting procedure at the very end
will empirically quantify which chunks behave badly due to ineffective
modeling of telluric lines and thus throw out or de-weigh the chunks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Future Work}\label{sec:future}

In terms of application to real observations, this brings marginal
improvements to existing Keck data. We tested on sig Dra, tau Ceti,
and M stars, the differences are...

Important for MINERVA, HRS2, HPF2. Crucial for CARMENES, HPF, EPDS, SHREK,
ESPRESSO, SPiRou etc. White paper has suggested improvement on line
lists in HITRAN. EPRV2 has a lot of recommendations. That is the
future direction.

### 2016-07-22 telluric/telluric.tex
Add all telluric plots and text from thesis.

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Impacts of Micro-tellurics on RV Precision}\label{sec:method}
-
-We performed end-to-end simulation of Keck data and analysis process
-to access the impacts of micro-tellurics on RV precision. We use Keck
-to demonstrate this because Keck has the highest precision. We chose
-sig Dra and tau Ceti as our stars because they are RV standards which
-have been observed hundreds of times with Keck/HIRES, and are also
-favorite RV standards at other precise RV facilities. I really want to
-add an M dwarf standard here as well!
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Methodology}
-
-We simulated Keck observations on sig Dra and tau Ceti by using
-synthetic stellar spectra of their respective spectral types (?) using
-SME (ZZZ cite Valenti and Fischer). We simulated one spectrum for each
-actual observed spectrum taken at Keck through the CPS programs. The
-synthetic stellar spectra is multiplied with the iodine atlas to
-create the standard iodine$+$ star RV observations. The multiplied
-spectrum is then multiplied with the blaze function and convolved with
-the observed spectral PSF, both derived from real observations for
-each night. Poisson noise is added.
-
-We then forward model the simulated spectra to extract RVs using the
-CPS Keck code (ZZZ cite Johnson and Howard). We used the synthetic
-stellar spectrum as the input stellar template. In reality, stellar
-templates are derived from observed stellar spectra via deconvolution,
-which would introduce additional errors. Using the same synthetic
-stellar spectrum would eliminate such errors and isolate the problem
-to telluric lines only.
-
-We ran two sets of simulations: control and contaminated. In the
-control, we only had stellar spectrum and iodine spectrum. In the
-contaminated, we added in simulated telluric lines in the simulated
-observed spectrum. The telluric lines were generated using TERRASPEC
-(ZZZ cite Bender). We adopted the typical Mauna Kea atmospheric
-condition (temperature and pressure profiles) and typical oxygen
-column density (which in realiaty flucturate very little anyway). For
-simplicity, we assumed the same water column density for every
-observation, which is pwv$=1$mm, a little bit humid than a typical
-Mauna Kea night (true? I think this is actually pretty typical). The
-pair of simulated control and contaminated spectra have the same added
-Poisson noise, and therefore any RV differences derived from these two
-sets of simulation would reveal the net effect of telluric
-contamination.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Results}
-
-Plots: RV difference vs. BC for sig Dra and tau Ceti. And M stars.
-
-Micro-tellurics in the iodine region introduces RMS$=0.6$ m/s scatter
-for GK stars (RV systematic error added in quadrature). Leaving
-untreated, this would define the precision floor.
-
-Additionally, it manifests as spurious signal at periods of a sidereal
-year and harmonics, with an amplitude of 20 cm/s. This would affect
-our ability to detect super-Earth in the habitable zone of GK stars
-(Earth's signal is 8 cm/s). We have seen such spurious signal in Keck
-data on many stars, and telluric contamination is one of the
-contributing factors (see discussion for other factors).
-
-For M stars... (probably worse)
+%----------------------------------------------------------------
+% Plot showing micro-telluric lines
+% made by ~/Exo../Keck../plots_general/spec_plot.pro
+\begin{figure}
+\includegraphics[scale=0.5]{telluric/tellurics_all.eps} 
+\caption{Telluric lines in the iodine region are mostly shallow water
+lines, with some moderately deep water lines near 5900\AA\ and very
+deep oxygen lines near 6300\AA. The insert plot is showing the
+pervasiveness of micro-telluric lines, i.e.~$\leq$1--3\% in depths.
+\label{telluric:fig:telluric}}
+\end{figure}
+%----------------------------------------------------------------
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Remedies and Effectiveness}
+\subsection{Characterization of the Impacts of Micro-tellurics on RV
+  Precision via Simulation}\label{keck:telluric:impact}
 
-Plots: effects of full forward modeling (RV difference between modeled
-and contaminated, modeled and control).
+% why Keck, why 185144 and 10700
+To evaluate the impacts of micro-tellurics (referred to often simply
+as ``tellurics'' below), we performed end-to-end simulation of \keck\
+data and analysis process on RV standard stars in order to isolate
+error sources. We use \keck\ data to for our study because Keck has
+the highest RV precision among all iodine-calibrated spectrometers,
+and it also has long observing baselines on a number of RV standard
+stars. RV standard stars are bright and quiet stars which do not host
+known planets, and thus exhibit the smallest RV variation in both
+short term and long term. Their data are often good diagnostic tools
+for identifying RV systematics. For our study, we used and simulated
+\keck\ RV spectra on two standard stars, $\sigma$ Draconis (HD 185144)
+and $\tau$ Ceti (HD 10700), which are benchmark classics in precise RV
+work.
 
-We demonstrate the effectiveness of several remedies. First, double
-masking: probably a terrible idea. Throwing away the pixels will make
-the fitter harder to converge, and introduce additional errors on the
-scales larger than the effects of telluric lines
-themselves. Additionally, it is hard to choose a flux cut-off
-level. Throwing away too much would mean unstable solution and lower
-RV precision, but masking too little would mean insufficient
-removal of tellurics.
+% more on the two stars 
+HD 185144 (spectral type G9V, per Simbad) has 712 \keck\ observations,
+with RV RMS $=$ 2.57 m/s, and it has a relatively small barycentric
+velocity (often referred to as the barycentric velocity correction, or
+BC; see Chapter~\ref{chap:doppler}) span, $[-4.7,\ 4.6]$ km/s, because
+it is near the north ecliptic pole. HD 10700 (spectral type G8.5V) has
+623 observations, with RMS $=$ 3.05 m/s, and its BC span is $[-27.8,\
+26.8]$ km/s. The RV RMS numbers quoted here come from reductions using
+our version of CPS Doppler pipeline, and they are larger than the RMS
+values from the most up-to-date CPS pipeline due to some recent
+improvements in the CPS version. The most recent CPS inventory (as of
+April 2016) also has a few new observations on these two stars.
 
-Second, full forward modeling plus some sort of masking for deep
-lines. This is the most effective way. Modeling precision of
-$\sim$90\% basically bring the adverse effects of tellurics down to
-$<$10 cm/s. 90\% is very easy to achieve -- remember the
-state-of-the-art is 1-2\%, and even consider errors induced by
-modeling residuals caused by atmospheric wind or lack of knowledge on
-linelist or broadening parameters or inaccurate knowledge on atmospheric
-temperature/pressure profiles. The deep lines may not be modeled very
-well. However, the statistical weighting procedure at the very end
-will empirically quantify which chunks behave badly due to ineffective
-modeling of telluric lines and thus throw out or de-weigh the chunks.
+We describe how we simulated our data and used them to characterize
+the impacts of tellurics in Section~\ref{keck:telluric:method}, and
+then lay out our results in Section~\ref{keck:telluric:results}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Methodology of the Simulation}\label{keck:telluric:method}
+
+% how we approach the problem with simulation
+The overall strategy is to bring out the effects of telluric
+contamination by comparing the extracted RVs from pairs of simulated
+observations: one with telluric absorption, and the other one in the
+pair without. For example, for HD 185144, we simulated two spectra for
+each of the 712 real observed spectrum. We then had two sets of
+simulated observations, one free of tellurics and one contaminated
+with tellurics. Next we ran the Doppler code on each set of 712
+spectra to extract RVs from them, and for the set with tellurics we
+used telluric-contaminated DSST and a telluric-free DSST for the
+telluric-free spectra. \\
+
+% how we simulated the spectrum
+Below is our recipe for simulating \keck\ spectra and DSSTs:
+\begin{enumerate}
+\item Generate a synthetic spectrum for the target star using
+  Spectroscopy Made Easy (SME;
+  \citealt{valentipiskunov1996,valentifischer2005}; the SME spectra are
+  kindly provided by Jason Curtis). We refer to this spectrum as the
+  input synthetic spectrum or the SME spectrum.
+\item Based on the SME spectrum, generate a deconcolved stellar
+  spectral template (DSST) for the target
+  star. First, we redshift the SME spectrum so that it has the same
+  barycentric velocity as the real DSST of the target star. Then we
+  break the SME spectrum into chunks as defined by the real DSST (an IDL
+  structure) of this target star.
+\item Run TERRASPEC \rev{\citep{Bender2012}, a versatile software for
+  synthesizing telluric spectrum (it is a wrapper around the HITRAN line
+  list \citep{hitran2013} and the LBLRTM package \citep{lblrtm},
+  developed by Chad Bender, who provided crucial help in this work for
+  using TERRASPEC)}, to generate a telluric absorption spectrum using a
+  typical Mauna Kea atmospheric condition in the summer, with
+  precipitable water vapor (pwv) 1~mm (a little bit more humid than
+  Keck's usual condition), and oxygen column density that is consistent
+  with the altitude of the real DSST observation. We multiply this
+  synthetic telluric spectrum with the SME spectrum to make a
+  telluric-contaminated DSST.
+\item Loop through each real observed spectrum of the target star, and
+  simulate a pair of observations following this recipe:
+  \begin{enumerate}
+  \item Shift the SME spectrum to have the same barycentric velocity
+    as the star at the epoch of the real observation (i.e., assuming
+    intrinsic stellar velocity is zero).
+  \item Generate a continuous wavelength solution for each echelle
+      order based on the best-fit wavelength solution for the real
+      spectrum. 
+  \item Re-sample the SME spectrum and the iodine atlas onto a
+    wavelength grid that is four times finer than the wavelength
+    solution grid. Multiply the stellar spectrum with the iodine
+    atlas.
+  \item To add telluric contamination: multiply the simulated spectrum
+    with a telluric absorption spectrum generated with TERRASPEC, again
+    for typical Mauna Kea summer, with pwv $=$ 1~mm, and oxygen column
+    density that is consistent with the altitude of the real observation.
+  \item Determine the IP for each echelle order with two options: (1)
+    a single Gaussian with $\sigma=1.7$ pixel, matching the \keck\
+    resolution; (2) a sum-of-Gaussian IP derived using the average IPs for
+    each echelle order. We will explain these two options later in the
+    text.
+  \item Convolve each order of the stellar$\times$iodine spectrum with
+    the IP.
+  \item Fit for the blaze function for each order of the real observed
+    spectrum with a third-order polynomial using the top 1\% of the flux,
+    and multiply the simulated spectrum so that they have matching ``blaze
+    functions''. This also ensures that the simulated spectrum has the
+    same photon counts as the real one.
+  \item Add photon noise according to Poisson statistics, when
+    desired.
+  \end{enumerate}
+\item Generate a separate data log file for each set of simulated of
+  observations under the same conditions (i.e., telluric choice, IP choice,
+  photon-noise choice).
+\end{enumerate}
+
+% different sets of simulations To isolate the problem of tellurics,
+we first simulated spectra free of photon noise and with a simple
+single Gaussian IP for the spectrograph ($\sigma = 1.7$ pixels to
+match the \keck\ resolution). When extracting RVs for such sets of
+simulated spectra, we fixed the IPs to the same as input and only
+fitted for three free parameters. This removes the errors induced by
+photon noise and uncertainties in IP fitting (which, after all,
+involves 12 additional free parameters). We then added the Poisson
+noise to the spectra, but still using simple and fixed IPs, to see how
+the effects will change in cases with limited-SNR (as opposed to
+infinite SNR). Next, we used complex IPs, the same ones as the
+best-fit sum-of-Gaussian IPs found for real spectra, and float the IP
+parameters when extracting RVs. \rev{For the simulated spectra with complex
+IPs, we extracted their RVs following exactly the same procedure for
+real observations, e.g., using IP initial guesses from solutions for
+real neighboring B star $+$ iodine observations.} The conditions and
+results of these three pairs of simulations are listed in
+Table~\ref{telluric:tab:simulation}, and also illustrated in
+Figure~\ref{telluric:fig:sim}. These results show the impacts of
+telluric contamination on \keck\ data, which is discussed in the
+following subsection.
+
+%----------------------------------------------------------------
+% Table: RV RMS for various simulations
+\renewcommand{\arraystretch}{1.2} % more row spacing for the table
+\begin{deluxetable}{ccccl}
+\tabletypesize{\scriptsize}
+\tablecaption{List of Simulations
+\label{telluric:tab:simulation}}
+\tablewidth{\textwidth}
+\tablehead{
+  \colhead{Simulation Conditions} & \colhead{Tellurics?} &
+  \colhead{185144 RMS} &
+  \colhead{10700 RMS} &
+  \colhead{More Details in} 
+}
+\startdata
+No photon noise, & No & 0.62 m/s & 1.95 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\ 
+simple, fixed IPs & Yes & 1.21 m/s & 2.42 m/s\tablenotemark{c} & top
+panels, Figure~\ref{telluric:fig:sim} \\ 
+\hline
+Poisson noise, & No & 2.11 m/s\tablenotemark{c} & 2.54 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\
+simple, fixed IPs\tablenotemark{a} & Yes & 2.12 m/s\tablenotemark{c} & 2.81 m/s\tablenotemark{c} &
+middle panels, Figure~\ref{telluric:fig:sim} \\ 
+\hline
+Poisson noise, & No & 1.22 m/s & 1.35 m/s & Section~\ref{keck:telluric:results}\\
+complex, floating IPs,\tablenotemark{a} & Yes & 1.29 m/s & 1.44 m/s &
+bottom panels, Figure~\ref{telluric:fig:sim} \\ 
+\hline
+Poisson noise, & No & 1.27 m/s & 1.43 m/s &Section~\ref{keck:telluric:masking} \\
+complex, floating IPs, & Yes & 1.27 m/s & 1.43 m/s & Figure~\ref{telluric:fig:dsstmask} \\
+masking the telluric pixels\tablenotemark{a} & & & & Table~\ref{telluric:tab:rmsmasking}  \\
+\hline 
+Poisson noise, & pwv $=$ 0.5, 0.9 & 1.28, 1.22 m/s & 1.32, 1.30 m/s &
+Section~\ref{keck:telluric:neid} \\ 
+complex, floating IPs, & pwv $=$ 1.0, 1.1 & 1.25, 1.23 m/s & 1.33, 1.31
+m/s & Figure~\ref{telluric:fig:neid} \\ 
+modeling tellurics\tablenotemark{b} 
+\enddata
+\tablenotetext{a}{With pairs of simulated spectra with or without
+  tellurics and each pair has the same Poisson noise added.}
+\tablenotetext{b}{Telluric lines added with pwv $=$ 1~mm, and we
+  extracted RVs using pwv $=$ 0.5, 0.9, 1.0, 1.1~mm to access how
+  accurately/precisely one needs to model the tellurics.}
+\tablenotetext{c}{These simulations suffer from severe numerical and
+  algorithmic errors for reasons not yet fully understood.}
+\end{deluxetable}
+%----------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Results of the Simulation}\label{keck:telluric:results}
+
+%----------------------------------------------------------------
+% Telluric effect, no photon noise
+% plot made by ~/Exo.../Keck.../simulate.../msplot.pro
+\begin{figure}
+\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rja01-rjb01.eps}}
+\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rja01-rjb01.eps}}\
+\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rjc01-rjd01.eps}}
+\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-rjc01-rjd01.eps}}\
+\subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-test0-test1.eps}}
+\subfloat{\includegraphics[scale=0.38]{telluric/10700-rv-bc-test0-test1.eps}}\
+\caption{Effects of telluric lines manifested as correlation between
+  RV and BC. Each point represents the difference in RV estimates for
+  a pair of simulated spectra: one without telluric absorption, and
+  one with telluric absorption on top of the stellar and iodine
+  spectra. {\bf Top 2 panels:} To isolate the effects of telluric
+  lines, the simulated spectra used for this plot do not have Poisson
+  noise added, and they have simple one-component Gaussian IPs which
+  have fixed width and thus the IP parameters are all fixed to the
+  true values in the RV extraction. {\bf Middle 2 panels:} same as the
+  top panels, but for simulated spectra with Poisson noise (same noise
+  for the telluric and non-telluric spectrum pairs; and still the same
+  simple IPs). {\bf Bottom 2 panels:} same as above, but for simulated
+  spectra with Poisson noise and complex IPs that are similar to the
+  ones in actual observations. IP parameters are not fixed in this
+  case, so the code is fitting 12 additional parameters for the IP on
+  top of the 3 for wavelength solution and Doppler shift (see
+  Chapter~\ref{chap:doppler} for more details on the code).
+\label{telluric:fig:sim}}
+\end{figure}
+%----------------------------------------------------------------
+
+% no photon noise
+Figure~\ref{telluric:fig:sim} illustrates the effects of telluric
+contamination under different conditions. The top panels are RV
+differences between the simulated spectrum pairs with infinite SNR and
+perfectly known IPs, which might somewhat represent the capability of
+future precise RV instruments. These two plots highlight the net
+effects of telluric contamination: they cause large biases in RV
+estimates, which manifest as strong RV-BC correlations or
+trends. \rev{Clearly, the current statistical weighting or ``vanking''
+procedure in the Doppler code is unable to fully correct these biases.}
+
+% adds photon noise?
+Interestingly, when we added in photon noise (middle panels of
+Figure~\ref{telluric:fig:sim}), the effects of telluric contamination
+are washed out significantly. \rev{This is probably because photon noise
+induces a much bigger RV scatter than the micro-telluric lines. This
+is not surprising, given that the depths of these micro-telluric lines
+are often comparable to noise level. We are still investigating the
+exact reason of this ``wash out''.}
+
+% adds complex IP 
+When using complex IPs and fitting for IPs in RV extraction (bottom
+panels of Figure~\ref{telluric:fig:sim}), the effects of telluric
+contamination are further washed out, as we are adding in more errors
+\rev{that are perhaps larger than telluric-induced ones}. We can
+barely see any RV-BC correlation in the case of HD 185144 and only
+some in HD 10700.
+
+% tellurics add RV RMS
+The RV-BC correlations shown in Figure~\ref{telluric:fig:sim} will
+translate into spurious peaks in the periodograms of the target star,
+and such spurious peaks will have periods around a sidereal year and
+its harmonics. This is very damaging for the search of exoplanets in
+the Habitable Zone around Sun-like stars, which would have periods
+around 360 days. Besides these spurious signals, telluric
+contamination also causes increases in RV RMS. In all cases of
+telluric-free and telluric-contaminated simulation pairs, the RV RMS
+is larger for the telluric-contaminated case
+(Table~\ref{telluric:tab:simulation}). The RMS numbers written in
+Figure~\ref{telluric:fig:sim} represent the amount of RV RMS added (in
+quadrature) because of telluric contamination (again, the spectrum
+pairs are same-noise pairs -- they only differ in terms of having or
+not having telluric lines). These numbers also represent an RV RMS
+floor set by the telluric contamination: for example, if we ignore
+tellurics in RV reduction, one would not achieve an RV precision of
+$<$0.6-0.7 m/s on G type stars using iodine cells as calibrators. This
+would compromise our ability to detect Earth or super-Earth exoplanets
+greatly (again, Earth 2.0 would have an RV amplitude of 0.08 m/s). In
+the next section, we discuss strategies to eliminate these adverse
+effects of telluric contamination for iodine-calibrated precise RV
+data.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion and Future Work}\label{sec:future}
+\subsection{Remedies and Effectiveness}\label{keck:telluric:remedies}
 
-In terms of application to real observations, this brings marginal
-improvements to existing Keck data. We tested on sig Dra, tau Ceti,
-and M stars, the differences are...
+There are several ways to remedy the adverse effects of telluric lines
+on RV precision and accuracy: masking, modeling, or a combination of
+both. Like the rest of this section, we focus our efforts on
+iodine-calibrated data. For ThAr-calibrated data, the current official
+HARPS pipeline masks deep telluric lines and abandons spectral orders
+that are heavily contaminated (Xavier Dumusque, private communication;
+\citealt{artigau2014}). \cite{2016AAS...22713719S} also discusses
+remedies and their effectiveness for ThAr-calibrated data in more band
+options including the near infrared.
 
-Important for MINERVA, HRS2, HPF2. Crucial for CARMENES, HPF, EPDS, SHREK,
-ESPRESSO, SPiRou etc. White paper has suggested improvement on line
-lists in HITRAN. EPRV2 has a lot of recommendations. That is the
-future direction.
+\subsubsection{Masking is an ineffective solution}\label{keck:telluric:masking}
+
+%----------------------------------------------------------------
+% Table: RV RMS for various simulations
+\renewcommand{\arraystretch}{1.2} % more row spacing for the table
+\begin{deluxetable}{ccl}
+\tabletypesize{\scriptsize}
+\tablecaption{Comparison of RV RMS between Simulations with or without Masking
+\label{telluric:tab:rmsmasking}}
+\tablewidth{320pt}
+\tablehead{
+  \colhead{HD 185144} & \colhead{HD 10700} & \colhead{Simulation Conditions}
+}
+\startdata
+1.22 m/s & 1.35 m/s & No tellurics \\
+1.29 m/s & 1.44 m/s & With tellurics \\
+1.27 m/s & 1.43 m/s & No tellurics, but masking telluric pixels \\
+1.27 m/s & 1.43 m/s & With tellurics, and masking telluric pixels
+\enddata
+\end{deluxetable}
+%----------------------------------------------------------------
+
+% what do I mean when I talk about masking?
+The simplest solution is to mask out telluric lines in the spectrum,
+which means, in practice, locate the telluric-contaminated pixels and
+flag them as bad pixels in the observed spectrum so that the
+least-$\chi^2$ fitter will ignore them. For \keck\ or any
+iodine-calibrated RV reduction, this also means masking out the
+regions corresponding to locations of telluric lines in the
+deconvolved stellar reference spectrum -- because the stellar
+reference spectrum was taken at a different BC, the telluric lines
+therein are shifted with respect to the ones in the epoch observation
+as we try to match up the stellar lines in observed and reference
+spectra. This double masking procedure is illustrated in
+Figure~\ref{telluric:fig:dsstmask}. This is done dynamically in
+the fitting process, in the sense that, for each iteration in the
+least-$\chi^2$ minimization process, the contaminated pixels are
+located according to the current wavelength solution parameters in
+this fitting iteration. The wavelength solution changes from iteration
+to iteration, and thus the masked pixels can change too.
+
+%----------------------------------------------------------------
+% Double masking of telluric lines
+% plot made by converting pdf to eps. pdf comes from slides of CfASSP
+% seminar talk, which can be found in ~/Ex.../Professional../..CfASSP../.
+\begin{figure}
+\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask1.eps}}\\
+\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask2.eps}}
+\caption{Illustration for how we mask telluric contaminated
+pixels. The top panel shows how we mask the telluric lines (red solid
+lines) in the epoch observation taken at $t=t_e$. The bottom panel
+shows why we also need to mask pixels associated with telluric lines
+in the deconvolved stellar reference spectrum taken at epoch $t=t_0$
+and being shifted in order to model the observation.
+\label{telluric:fig:dsstmask}}
+\end{figure}
+%----------------------------------------------------------------
+
+% simulations and results 
+To investigate the effectiveness of masking, we performed RV
+extraction on simulated spectra with or without telluric lines
+injected and with or without masking (all with Poisson noise and
+complex IP to mimic real observations as much as possible). For
+stellar reference spectrum, we used the synthetic spectrum with
+telluric lines. The results are already listed in
+Table~\ref{telluric:tab:simulation}, but are listed again in
+Table~\ref{telluric:tab:rmsmasking} for clear comparisons. In terms of
+improving RV precision or reducing RV RMS, masking is very
+ineffective. The additional errors it introduces diminish its
+merits. On the other hand, masking does improve the accuracy to some
+degree: for example, masking does remove the downward RV trend seen in
+HD 10700 data on the bottom right plot of
+Figure~\ref{telluric:fig:sim} in the BC range $[-3\times10^4,\
+-2\times10^4]$ m/s. However, masking is an ineffective way to mitigate
+the effects of telluric contamination overall, especially since the RV
+errors and RV-BC trends are dominated by photon noise and algorithmic
+errors (and other types of errors too in real observations).
+
+% why simple masking would not work for high precision/accuracy So why
+masking does not work? First of all, it complicates the $\chi^2$
+surface and ``breaks'' the L-M fitter. Due to the dynamic nature of
+the mask mentioned above, the degrees of freedom for fitting could
+change, because some telluric lines may shift in and out of this
+spectral chunk as the wavelength solution changes. This would make the
+fitter harder to converge or may create more local minima in which the fitter
+can get stuck, causing additional errors. \rev{A better fitter might
+solve the convergence problem, but it is hard to justify throwing away
+useful iodine and stellar content embedded in the masked pixels.}
+Finally, to mask the telluric lines out, one needs to pick a flux
+threshold for the masks. This threshold must maintain a balance
+between masking too much (throwing away too much iodine and stellar
+information) and too little (leaving shallow telluric lines and line
+wings untreated). In our study, we have chosen a flux threshold of
+0.3\%, which means any pixel with telluric absorption deeper than
+0.3\% will be masked (reference telluric spectrum is generated by
+TERRASPEC at an zenith angel of 70$^{\degree}$, meaning deep oxygen
+lines, and with pwv $=$ 0.8~mm, a little more than typical \keck\
+humidity). This masks 11\% of the spectral domain, which is quite
+substantial and is very damaging to the RV precision, but is almost
+the minimal amount of masking required to achieve some RV accuracy
+improvement \rev{as we found out by testing various masking depths}.
+
+% how about masking in real observations?  
+We also applied telluric masking in RV reduction for real
+observations, and saw no improvement over RV precision or
+accuracy. This is because other effects dominate rather than
+tellurics, as mentioned above, such as photon and algorithmic errors
+and especially deconvolution errors in stellar reference spectrum,
+which are discussed in Section~\ref{keck:sec:dsst} and
+\ref{keck:sec:algorithm}.
+
+% summarize
+To summarize, masking sounds like a simple solution to the problem of
+micro-telluric contamination, but it is actually complicated to
+implement (for iodine-calibrated RV reduction) and it is ineffective
+in terms of improving RV precision. We do not recommend masking as a
+remedy for treating micro-telluric lines in iodine-calibrated RV
+work. We believe the most effective way is to forward model telluric
+lines, and combine that with some ``masking'' for deep or troublesome
+telluric lines, which we discuss in the next subsection.
+
+\subsubsection{How precisely does one need to model the tellurics?}\label{keck:telluric:neid}
+
+%----------------------------------------------------------------
+% NEID Plot showing how much you need to model tellurics
+\begin{figure}
+\includegraphics[scale=0.5]{telluric/neid.eps} 
+\caption{\rev{Improvements in RV RMS for different ``level" of telluric
+  modeling/removal.} For example, the mid point labeled with ``50\%, 40 cm/s"
+  means that if you model your telluric absorption lines to 50\% of
+  their original depths, the effects of the residual telluric
+  absorption will add 40 cm/s in quadrature to your final RV RMS. The
+  blue point marks the RV RMS for simulations with Poisson noise and
+  complex IP on HD 185144, which represents the photon-limited RV
+  precision (subject to additional numeric or algorithmic errors; see
+  Chapter~\ref{chap:conclusion} for more on the limitation of the
+  Doppler code).
+\label{telluric:fig:neid}}
+\end{figure}
+%----------------------------------------------------------------
+
+% modeling is the way to go
+The other way is to incorporate telluric lines as part of the iodine
+RV forward modeling process, where water column density can either be
+from a priori knowledge or an additional free parameter. In principle,
+the oxygen column density can also be a free parameter, not because
+the amount of oxygen varies on a noticeable level, but just to allow
+some compensation for errors in atmospheric temperature and pressure
+profile and so on, \rev{in order to model the oxygen lines more
+precisely}. We do not fit for oxygen in our simulation or treatment
+for real observations in this work for simplicity, and also because
+the chunks contaminated with oxygen lines are in the reddest part near
+6300\AA, where the amount of iodine and stellar contents are minimal
+anyway, and these chunks tend to be thrown away or heavily de-weighted
+in the final RV weighting process.
+
+% the goal of modeling
+Modeling telluric absorption lines to high precision (below 1--2\% RMS
+residual) can be a challenging task. There are several reasons for
+this: lab measurements of a large number of water lines are
+inaccurate, in terms of line depths, line positions, and line shapes;
+and these line properties can also be uncertain due to change or a
+lack of knowledge of the atmospheric conditions, such as wind, high
+line-of-sight variations (e.g., water vapor), and mixing
+uncertainties. For a summary of the state of the problem and paths
+forward recommended by the RV community, see Section~4.6 in
+\cite{eprv2015}. However, the goal here is not to model or remove
+the telluric lines perfectly, but to mitigate their impact on RV
+precision and accuracy as much as possible. A central question is: how
+well do we need to model telluric lines to reach a certain RV
+precision \citep{eprv2015}?
+
+% how well should we model?  
+To answer this question under the context of iodine-calibrated RV, we
+performed RV extractions on the simulated HD 185144 data with telluric
+absorption (all with pwv $=$ 1.0~mm, as described in
+Section~\ref{keck:telluric:method}), incorporating forward modeling of
+telluric lines with different levels of accuracy and using a stellar
+reference spectrum free of tellurics. The results are illustrated in
+Figure~\ref{telluric:fig:neid}. All three simulations were run with
+simulated spectra of HD 185144 with pwv 1.0~mm, but the one labeled
+``0\%'' has no telluric modeling in the RV extraction, while the one
+labeled with ``50\%'' has synthetic telluric lines with pwv 0.5~mm in
+the forward modeling process, \rev{and ``90\%'' meaning using telluric
+model with pwv 0.9~mm. In addition, we also used telluric model with
+pwv 1.0~mm and 1.1~mm in the forward modeling, which produced similar
+RV RMS as the ``90\%'' simulation with no visible RV-BC trends or
+correlations. A $\sim$90\% modeling accuracy for the water lines would
+control the RV RMS contribution from tellurics to below 20~cm/s, which
+is near the target precision for the next generation RV
+spectrographs. This level of modeling precision is very easy to
+achieve in reality. However, it is worrisome that even 100\% modeling
+with pwv 1.0~mm cannot eliminate the increase in RV RMS completely. To
+improve beyond 20 cm/s, we think that a next-generation Doppler code
+is needed.}
+
+% well actually vanking did a lot of heavy lifting
+One important point to notice is that the reason why the damage of
+10\% telluric modeling residual is controlled down to $\leq$20~cm/s is
+the additional masking and weighting process in the Doppler code,
+i.e., ``vanking'' (Chapter~\ref{chap:doppler}). A
+combination of modeling (even only to 90\% precision) and statistical
+weighting can effectively control the RV RMS introduced by tellurics
+to $\leq$20~cm/s. Weighting plays a role in telluric contamination
+remedy because it is essentially performing some masking on the
+chunks that are badly contaminated by tellurics and/or have large
+modeling residuals, such as the ones near 6300\AA\ with deep oxygen
+lines and little stellar or iodine content. Chunks with deep and
+numerous oxygen lines are normally thrown out completely, and other
+contaminated chunks which suffer from low precision will receive lower
+weights and thus cast a lower impact on the final precision and
+accuracy. In reality, we are using a combination of modeling and
+masking or weighting to tackle problem of telluric contamination,
+which we believe is the optimal solution for iodine-calibrated RVs.
+
+\subsubsection{Treating telluric contamination in real observations}\label{keck:telluric:real}
+
+%----------------------------------------------------------------
+% Effect of clean DSST and preliminary modeling with real data
+% plot made by ~/Exo.../Keck.../plots_general/basic_rv.pro, choice='3panel'
+\begin{figure}
+\subfloat[HD 185144, rj82 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj82_3panel.eps}}\
+\subfloat[HD 185144, rj172 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj172_3panel.eps}}\
+\subfloat[HD 10700, rj82 template]{\includegraphics[scale=0.42]{telluric/10700_BC_RV_rj82_3panel.eps}}\
+\caption{Effects of using clean DSST and preliminary telluric modeling
+  on RV precision and accuracy, for HD 185144 (top two rows) and HD
+  10700 (bottom row). There are two sets of data for HD 185144 because
+  we ran the Doppler code with two DSSTs derived from spectra taken at
+  two different epochs (i.e., at different BCs). The left and middle
+  panels are showing RVs vs.\ BCs for RV extractions with and without
+  telluric treatment, respectively. The right panels show the RV
+  difference between the two panels.
+\label{telluric:fig:real}}
+\end{figure}
+%----------------------------------------------------------------
+
+% what should we do about real observations?
+The situation is much more complicated for real observations, because
+other noise sources enter the picture, some uncontrollable and/or
+unknown. It turns out that telluric contamination is {\em not} the
+dominant sources of RV systematic errors in \keck\ data. We later
+found out that the major culprit behind the RV-BC correlation patterns
+is probably errors in the DSSTs, which are discussed in
+Section~\ref{keck:sec:dsst}. This fact makes it somewhat difficult to
+assess the effectiveness of telluric treatment on real data, but the
+simulations have demonstrated that the the best and most effective strategy
+is to have a clean DSST and to forward model the telluric lines (and
+also to mask out deep lines and de-weight chunks with hard-to-clean
+tellurics, which are already taken care of by vanking).
+
+\begin{comment}
+We have tested both masking and preliminary
+modeling: In the case of HD 185144, RV RMS went down (from
+2.57 m/s) after we applied masking (to 2.44 m/s) or modeling (to 2.50
+m/s), with visible changes in the RV-BC trends. In the case of HD
+10700, the RV RMS actually went up (from 3.05 m/s) after masking (to
+3.26 m/s) or modeling (3.17 m/s), also with visible changes in the
+RV-BC trend.
+\end{comment}
+
+% our best efforts...
+Figure~\ref{telluric:fig:real} represents our best efforts so far and
+their effects. Our treatment plan includes using ``cleaned'' DSSTs (we
+describe how we cleaned the DSSTs later in this subsection) and
+preliminary modeling of telluric lines in the Doppler code, where we
+used pwv $=$ 1.0 mm for all observations instead of fitting pwv for
+each one. In the case of HD 185144, the RV RMS values decreased after
+we treated the tellurics, but it is not the case for HD 10700 -- we
+suspect that the difference comes from the choice of the pwv value of
+1~mm, which is more typical for HD 185144 observations but perhaps not
+so for HD 10700 (these two stars are at very different
+Declinations). We plan to model the water absorption in each
+observation using best-fit or best-estimated pwv in the near future.
+
+% DSST and how we cleaned it
+How about telluric lines in the DSST? For simulations, we have the
+privilege of using the synthetic spectrum which is naturally
+telluric-free. For real observations, telluric contamination enters
+every observed spectrum associated with the making of DSST (for a
+detailed description of how the DSST is made, see
+Section~\ref{doppler:sec:reference}). To remove errors in the DSST
+caused by the telluric contamination, we formulated a recipe to
+``clean up'' the DSST:
+
+\begin{enumerate}
+\item When fitting the bracketing B star $+$ iodine observations, we
+  incorporate synthetic telluric lines generated by TERRASPEC as one of
+  the input reference spectra (just like the iodine atlas). The water
+  column density, or pwv, is determined by fitting two rich water bands
+  among the spectrum taken by the red chip data of \keck\
+  (7000-8000\AA). Although we use Mauna Kea's typical atmospheric
+  condition and adjust oxygen column density according to observation
+  altitude, we still fit for oxygen column density to allow some room
+  for errors in the model (the adjustment needed is typically $<$0.5\%).
+\item Using the IPs and wavelength solution derived in step (1), we
+  run the deconvolution algorithm and generate a DSST, which would
+  have telluric lines in it because telluric lines exist in the
+  stellar (iodine-free) spectra.
+\item We divide out the telluric lines in the DSST in two steps: 
+  \begin{enumerate}
+  \item Fitting two parameters to make sure the telluric lines match
+    the ones in DSST: broadening parameter (width of a Gaussian
+    kernel) and wavelength shift. The broadening parameter is
+    necessary because the synthetic telluric lines are at an extremely
+    high resolution, while the telluric lines in the DSST are
+    deconvolved but are typically lower. The wavelength shift is
+    needed because the wavelengths of the telluric lines, provided by
+    the wavelength solution of the DSST, could differ from rest-frame
+    telluric line wavelengths because of errors in DSST or changing
+    atmospheric conditions such as wind. 
+  \item Fitting these two parameters is not a straightforward
+    least-$\chi^2$ problem, because stellar lines are also present in the
+    spectrum and we do not have an input model for them. Thus, instead of
+    minimizing residuals between model (broadened and shifted telluric
+    lines) and data (deconvolved telluric lines plus stellar lines), we
+    minimize the flux above the continuum level to \rev{optimize the parameters
+    and the telluric model. In the future, we hope to incorporate this
+    into the code for making DSSTs (see Chapter~\ref{chap:doppler}), i.e.,
+    fitting for telluric lines and stellar lines at the same time.}
+  \item We divide out the best-fit telluric model from the DSST to
+    obtain a cleaned DSST.
+  \end{enumerate}
+\end{enumerate}
+
+Naturally, this process does not clean up the DSST perfectly,
+especially for deep and moderately deep lines, where the line profiles
+are hard to match. We hope to improve this cleaning process, as well
+as the entire process for making DSSTs, which we discuss in
+Section~\ref{keck:sec:conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Summary of Recommendations on Treating Telluric
+  Contamination}\label{keck:telluric:summary}
+
+As argued and tested in the previous subsections, to effectively
+eliminate the adverse effects of telluric contamination in
+iodine-calibrated precise RV data, we recommend the following
+strategies:
+\begin{itemize}
+  \item Masking deep and saturated lines and wings liberally, or
+    deserting such spectral regions completely.
+  \item Creating DSST following the recipe described in
+    Section~\ref{keck:telluric:real}, i.e.\ modeling ``out'' telluric
+    lines in every step. 
+  \item Incorporating forward modeling of telluric lines in the RV
+    extraction process.
+  \item Assigning low statistical weights to RVs reported by
+    telluric-contaminated spectral regions which suffer from low RV
+    precision and accuracy.
+\end{itemize}
+
+We plan to run simulations on an M star, HD 95735, also an RV
+standard. M stars are particularly interesting because they may be
+more susceptible to telluric contamination -- they have more stellar
+lines in the red where the telluric lines are denser. We also plan to
+implement full forward-modeling of telluric lines in real data
+reduction (as opposed to our toy modeling with fixed water column
+density for all dates/observations), and find out whether a priori or
+floating water column density parameter works better. We plan to
+improve the DSST cleaning process by incorporating forward modeling of
+telluric lines in the ``piston Gaussians deconvolver'' that is
+currently used for making DSST, instead of dividing them out. We hope
+to implement our telluric correction package into the official CPS
+pipeline eventually, which will be busily processing \keck\ follow-up
+data on TESS targets (many M dwarfs, undoubtedly) in the near future.

### 2016-08-17 telluric/telluric.tex
Migrate thesis text in and adjust formats etc.

@@
 RV, especially for the micro-telluric lines. ZZZ We first describe our
-methodology for characterizing the effects of tellurics in
-Section~\ref{sec:method}, then... ZZZ
+methodology for characterizing the effects of tellurics in, then... ZZZ
 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{telluric/tellurics_all.eps} 
+\includegraphics[scale=0.3]{telluric/tellurics_all.eps} 
 \caption{Telluric lines in the iodine region are mostly shallow water
@@
 pervasiveness of micro-telluric lines, i.e.~$\leq$1--3\% in depths.
-\label{telluric:fig:telluric}}
+\label{fig:telluric}}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Characterization of the Impacts of Micro-tellurics on RV
-  Precision via Simulation}\label{keck:telluric:impact}
+\section{Characterization of the Impacts of Micro-tellurics on RV
+  Precision via Simulation}\label{sec:impact}
 
@@
 velocity (often referred to as the barycentric velocity correction, or
-BC; see Chapter~\ref{chap:doppler}) span, $[-4.7,\ 4.6]$ km/s, because
+BC) span, $[-4.7,\ 4.6]$ km/s, because
 it is near the north ecliptic pole. HD 10700 (spectral type G8.5V) has
@@
 We describe how we simulated our data and used them to characterize
-the impacts of tellurics in Section~\ref{keck:telluric:method}, and
-then lay out our results in Section~\ref{keck:telluric:results}.
+the impacts of tellurics in Section~\ref{sec:method}, and
+then lay out our results in Section~\ref{sec:results}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Methodology of the Simulation}\label{keck:telluric:method}
+\subsection{Methodology of the Simulation}\label{sec:method}
 
@@
   typical Mauna Kea atmospheric condition in the summer, with
-  precipitable water vapor (pwv) 1~mm (a little bit more humid than
-  Keck's usual condition), and oxygen column density that is consistent
+  precipitable water vapor (pwv) 1~mm\footnote{As reported at
+    \href{http://www.cfht.hawaii.edu/Instruments/ObservatoryManual/CFHT_ObservatoryManual_(Sec_2).html}{CFHT
+  website}.}, and oxygen column density that is consistent
   with the altitude of the real DSST observation. We multiply this
@@
 results of these three pairs of simulations are listed in
-Table~\ref{telluric:tab:simulation}, and also illustrated in
-Figure~\ref{telluric:fig:sim}. These results show the impacts of
+Table~\ref{tab:simulation}, and also illustrated in
+Figure~\ref{fig:sim}. These results show the impacts of
 telluric contamination on \keck\ data, which is discussed in the
@@
 \renewcommand{\arraystretch}{1.2} % more row spacing for the table
-\begin{deluxetable}{ccccl}
+\begin{deluxetable*}{ccccl}
+  \centering
 \tabletypesize{\scriptsize}
 \tablecaption{List of Simulations
-\label{telluric:tab:simulation}}
+\label{tab:simulation}}
 \tablewidth{\textwidth}
@@
 \startdata
-No photon noise, & No & 0.62 m/s & 1.95 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\ 
+No photon noise, & No & 0.62 m/s & 1.95 m/s\tablenotemark{c} & Section~\ref{sec:results} \\ 
 simple, fixed IPs & Yes & 1.21 m/s & 2.42 m/s\tablenotemark{c} & top
-panels, Figure~\ref{telluric:fig:sim} \\ 
+panels, Figure~\ref{fig:sim} \\ 
 \hline
-Poisson noise, & No & 2.11 m/s\tablenotemark{c} & 2.54 m/s\tablenotemark{c} & Section~\ref{keck:telluric:results} \\
+Poisson noise, & No & 2.11 m/s\tablenotemark{c} & 2.54 m/s\tablenotemark{c} & Section~\ref{sec:results} \\
 simple, fixed IPs\tablenotemark{a} & Yes & 2.12 m/s\tablenotemark{c} & 2.81 m/s\tablenotemark{c} &
-middle panels, Figure~\ref{telluric:fig:sim} \\ 
+middle panels, Figure~\ref{fig:sim} \\ 
 \hline
-Poisson noise, & No & 1.22 m/s & 1.35 m/s & Section~\ref{keck:telluric:results}\\
+Poisson noise, & No & 1.22 m/s & 1.35 m/s & Section~\ref{sec:results}\\
 complex, floating IPs,\tablenotemark{a} & Yes & 1.29 m/s & 1.44 m/s &
-bottom panels, Figure~\ref{telluric:fig:sim} \\ 
+bottom panels, Figure~\ref{fig:sim} \\ 
 \hline
 Poisson noise, & No & 1.27 m/s & 1.43 m/s &Section~\ref{keck:telluric:masking} \\
-complex, floating IPs, & Yes & 1.27 m/s & 1.43 m/s & Figure~\ref{telluric:fig:dsstmask} \\
-masking the telluric pixels\tablenotemark{a} & & & & Table~\ref{telluric:tab:rmsmasking}  \\
+complex, floating IPs, & Yes & 1.27 m/s & 1.43 m/s & Figure~\ref{fig:dsstmask} \\
+masking the telluric pixels\tablenotemark{a} & & & & Table~\ref{tab:rmsmasking}  \\
 \hline 
 Poisson noise, & pwv $=$ 0.5, 0.9 & 1.28, 1.22 m/s & 1.32, 1.30 m/s &
-Section~\ref{keck:telluric:neid} \\ 
+Section~\ref{sec:model} \\ 
 complex, floating IPs, & pwv $=$ 1.0, 1.1 & 1.25, 1.23 m/s & 1.33, 1.31
-m/s & Figure~\ref{telluric:fig:neid} \\ 
+m/s & Figure~\ref{fig:neid} \\ 
 modeling tellurics\tablenotemark{b} 
@@
   algorithmic errors for reasons not yet fully understood.}
-\end{deluxetable}
+\end{deluxetable*}
 %----------------------------------------------------------------
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Results of the Simulation}\label{keck:telluric:results}
+\subsection{Results of the Simulation}\label{sec:results}
 
@@
 % plot made by ~/Exo.../Keck.../simulate.../msplot.pro
-\begin{figure}
+\begin{figure*}
+  \centering
 \subfloat{\includegraphics[scale=0.38]{telluric/185144-rv-bc-rja01-rjb01.eps}}
@@
   case, so the code is fitting 12 additional parameters for the IP on
-  top of the 3 for wavelength solution and Doppler shift (see
-  Chapter~\ref{chap:doppler} for more details on the code).
-\label{telluric:fig:sim}}
-\end{figure}
+  top of the 3 for wavelength solution and Doppler shift.
+\label{fig:sim}}
+\end{figure*}
 %----------------------------------------------------------------
@@
 % no photon noise
-Figure~\ref{telluric:fig:sim} illustrates the effects of telluric
+Figure~\ref{fig:sim} illustrates the effects of telluric
 contamination under different conditions. The top panels are RV
@@
 Interestingly, when we added in photon noise (middle panels of
-Figure~\ref{telluric:fig:sim}), the effects of telluric contamination
+Figure~\ref{fig:sim}), the effects of telluric contamination
 are washed out significantly. \rev{This is probably because photon noise
@@
 When using complex IPs and fitting for IPs in RV extraction (bottom
-panels of Figure~\ref{telluric:fig:sim}), the effects of telluric
+panels of Figure~\ref{fig:sim}), the effects of telluric
 contamination are further washed out, as we are adding in more errors
@@
 % tellurics add RV RMS
-The RV-BC correlations shown in Figure~\ref{telluric:fig:sim} will
+The RV-BC correlations shown in Figure~\ref{fig:sim} will
 translate into spurious peaks in the periodograms of the target star,
@@
 is larger for the telluric-contaminated case
-(Table~\ref{telluric:tab:simulation}). The RMS numbers written in
-Figure~\ref{telluric:fig:sim} represent the amount of RV RMS added (in
+(Table~\ref{tab:simulation}). The RMS numbers written in
+Figure~\ref{fig:sim} represent the amount of RV RMS added (in
 quadrature) because of telluric contamination (again, the spectrum
@@
 \tablecaption{Comparison of RV RMS between Simulations with or without Masking
-\label{telluric:tab:rmsmasking}}
-\tablewidth{320pt}
+\label{tab:rmsmasking}}
+\tablewidth{280pt}
 \tablehead{
@@
 1.29 m/s & 1.44 m/s & With tellurics \\
-1.27 m/s & 1.43 m/s & No tellurics, but masking telluric pixels \\
-1.27 m/s & 1.43 m/s & With tellurics, and masking telluric pixels
+1.27 m/s & 1.43 m/s & No tellurics; with masking \\
+1.27 m/s & 1.43 m/s & With tellurics; with masking
 \enddata
@@
 spectra. This double masking procedure is illustrated in
-Figure~\ref{telluric:fig:dsstmask}. This is done dynamically in
+Figure~\ref{fig:dsstmask}. This is done dynamically in
 the fitting process, in the sense that, for each iteration in the
@@
 \begin{figure}
-\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask1.eps}}\\
-\subfloat{\includegraphics[scale=0.5]{telluric/dsst-mask2.eps}}
+\subfloat{\includegraphics[scale=0.3]{telluric/dsst-mask1.eps}}\\
+\subfloat{\includegraphics[scale=0.3]{telluric/dsst-mask2.eps}}
 \caption{Illustration for how we mask telluric contaminated
@@
 and being shifted in order to model the observation.
-\label{telluric:fig:dsstmask}}
+\label{fig:dsstmask}}
 \end{figure}
@@
 telluric lines. The results are already listed in
-Table~\ref{telluric:tab:simulation}, but are listed again in
-Table~\ref{telluric:tab:rmsmasking} for clear comparisons. In terms of
+Table~\ref{tab:simulation}, but are listed again in
+Table~\ref{tab:rmsmasking} for clear comparisons. In terms of
 improving RV precision or reducing RV RMS, masking is very
@@
 HD 10700 data on the bottom right plot of
-Figure~\ref{telluric:fig:sim} in the BC range $[-3\times10^4,\
+Figure~\ref{fig:sim} in the BC range $[-3\times10^4,\
 -2\times10^4]$ m/s. However, masking is an ineffective way to mitigate
@@
 tellurics, as mentioned above, such as photon and algorithmic errors
-and especially deconvolution errors in stellar reference spectrum,
-which are discussed in Section~\ref{keck:sec:dsst} and
-\ref{keck:sec:algorithm}.
+and especially deconvolution errors in stellar reference spectrum.
 
@@
 
-\subsubsection{How precisely does one need to model the tellurics?}\label{keck:telluric:neid}
+%----------------------------------------------------------------
+\subsection{How precisely does one need to model the tellurics?}\label{sec:model}
 
@@
 \begin{figure}
-\includegraphics[scale=0.5]{telluric/neid.eps} 
+  \centering
+\includegraphics[scale=0.3]{telluric/neid.eps} 
 \caption{\rev{Improvements in RV RMS for different ``level" of telluric
@@
   complex IP on HD 185144, which represents the photon-limited RV
-  precision (subject to additional numeric or algorithmic errors; see
-  Chapter~\ref{chap:conclusion} for more on the limitation of the
-  Doppler code).
-\label{telluric:fig:neid}}
+  precision (subject to additional numeric or algorithmic errors).
+\label{fig:neid}}
 \end{figure}
@@
 absorption (all with pwv $=$ 1.0~mm, as described in
-Section~\ref{keck:telluric:method}), incorporating forward modeling of
+Section~\ref{sec:method}), incorporating forward modeling of
 telluric lines with different levels of accuracy and using a stellar
 reference spectrum free of tellurics. The results are illustrated in
-Figure~\ref{telluric:fig:neid}. All three simulations were run with
+Figure~\ref{fig:neid}. All three simulations were run with
 simulated spectra of HD 185144 with pwv 1.0~mm, but the one labeled
@@
 the additional masking and weighting process in the Doppler code,
-i.e., ``vanking'' (Chapter~\ref{chap:doppler}). A
+i.e., ``vanking''. A
 combination of modeling (even only to 90\% precision) and statistical
@@
 
-\subsubsection{Treating telluric contamination in real observations}\label{keck:telluric:real}
+\subsubsection{Treating telluric contamination in real observations}\label{sec:real}
 
@@
 % plot made by ~/Exo.../Keck.../plots_general/basic_rv.pro, choice='3panel'
-\begin{figure}
-\subfloat[HD 185144, rj82 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj82_3panel.eps}}\
-\subfloat[HD 185144, rj172 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj172_3panel.eps}}\
-\subfloat[HD 10700, rj82 template]{\includegraphics[scale=0.42]{telluric/10700_BC_RV_rj82_3panel.eps}}\
+\begin{figure*}
+\subfloat[HD 185144, rj82 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj82_3panel.eps}}\\
+\subfloat[HD 185144, rj172 template]{\includegraphics[scale=0.42]{telluric/185144_BC_RV_rj172_3panel.eps}}\\
+\subfloat[HD 10700, rj82 template]{\includegraphics[scale=0.42]{telluric/10700_BC_RV_rj82_3panel.eps}}
 \caption{Effects of using clean DSST and preliminary telluric modeling
@@
   difference between the two panels.
-\label{telluric:fig:real}}
-\end{figure}
+\label{fig:real}}
+\end{figure*}
 %----------------------------------------------------------------
@@
 % our best efforts...
-Figure~\ref{telluric:fig:real} represents our best efforts so far and
+Figure~\ref{fig:real} represents our best efforts so far and
 their effects. Our treatment plan includes using ``cleaned'' DSSTs (we
@@
 detailed description of how the DSST is made, see
-Section~\ref{doppler:sec:reference}). To remove errors in the DSST
+Appendix? ZZZ To remove errors in the DSST
 caused by the telluric contamination, we formulated a recipe to
@@
     and the telluric model. In the future, we hope to incorporate this
-    into the code for making DSSTs (see Chapter~\ref{chap:doppler}), i.e.,
+    into the code for making DSSTs, i.e.,
     fitting for telluric lines and stellar lines at the same time.}
@@
 are hard to match. We hope to improve this cleaning process, as well
-as the entire process for making DSSTs, which we discuss in
-Section~\ref{keck:sec:conclusion}.
+as the entire process for making DSSTs. We plan
+to run simulations on an M star, HD 95735, also an RV standard. M stars
+are particularly interesting because they may be more susceptible to
+telluric contamination -- they have more stellar lines in the red
+where the telluric lines are denser. We also plan to implement full
+forward-modeling of telluric lines in real data reduction (as opposed
+to our toy modeling with fixed water column density for all
+dates/observations), and find out whether a priori or floating water
+column density parameter works better. We plan to improve the DSST
+cleaning process by incorporating forward modeling of telluric lines
+in the ``piston Gaussians deconvolver'' that is currently used for
+making DSST, instead of dividing them out. We hope to implement our
+telluric correction package into the official CPS pipeline eventually,
+which will be busily processing \keck\ follow-up data on TESS targets
+(many M dwarfs, undoubtedly) in the near future.
 
@@
 \subsection{Summary of Recommendations on Treating Telluric
-  Contamination}\label{keck:telluric:summary}
+  Contamination}\label{sec:summary}
 
@@
   \item Creating DSST following the recipe described in
-    Section~\ref{keck:telluric:real}, i.e.\ modeling ``out'' telluric
+    Section~\ref{sec:real}, i.e.\ modeling ``out'' telluric
     lines in every step. 
